---
title: "Kiln Data"
author: "Edward Yu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: paper
    highlight: textmate
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo    = TRUE,
                      error   = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      cache   = TRUE,
                      fig.width = 8, fig.height = 5,
                      dpi = 180)
rm(list = ls())

# load stuff
library(tidyverse)
library(plotly)

theme_set(theme_minimal())

source("../src/kilnFunctions.R")
source("../src/userFunctions.R")

# import data -------------------------------------------------------------
df_merged    <- read_csv("../data/processed_data/df_merged.csv")
df_yields    <- read_csv("../data/processed_data/df_yields.csv")
df_defects   <- read_csv("../data/processed_data/df_defects.csv")
kilns_AB  <- read_csv("../data/processed_data/kilns_AB.csv") %>% mutate_if(is.character,as.factor)
kilns_C   <- read_csv("../data/processed_data/kilns_C.csv")  %>% mutate_if(is.character,as.factor)
kilns_D   <- read_csv("../data/processed_data/kilns_D.csv")  %>% mutate_if(is.character,as.factor)
kilns_E   <- read_csv("../data/processed_data/kilns_E.csv")  %>% mutate_if(is.character,as.factor)
kilns_F   <- read_csv("../data/processed_data/kilns_F.csv")  %>% 
  mutate_if(is.character,as.factor) %>% 
  mutate(kiln = as.factor("F"))
kilns_G   <- read_csv("../data/processed_data/kilns_G.csv")  %>% mutate_if(is.character,as.factor)
kilns_H   <- read_csv("../data/processed_data/kilns_H.csv")  %>% mutate_if(is.character,as.factor)

allAucValues <- read_csv("../data/processed_data/kilnsAucValues.csv")

# join kiln AUC to original data ------------------------------------------
df_merged_auc <- df_merged %>% 
  left_join(allAucValues, by='LOTNO') %>% 
  dplyr::mutate_if(is.character, as.factor) %>% 
  mutate(LOTNO = as.factor(LOTNO),
         ITEM = as.factor(ITEM)) %>%
  na.omit(aucDiff)

df_yields_auc <- df_yields %>% 
  left_join(allAucValues, by='LOTNO') %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(LOTNO = as.factor(LOTNO),
         ITEM = as.factor(ITEM)) %>% 
  mutate(LOTNO = as.factor(LOTNO))%>% 
  na.omit(aucDiff)

df_defects_auc <- df_defects %>% 
  left_join(allAucValues, by='LOTNO') %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(LOTNO = as.factor(LOTNO),
         ITEM = as.factor(ITEM)) %>% 
  mutate(LOTNO = as.factor(LOTNO))%>% 
  na.omit(aucDiff)
```

# Cleaned data {.tabset .tabset-pills .tabset-fade}

Imported and cleaned all kiln data available from 2018-2020. Involved using an algorithm to remove high peaks and valleys, detection of when the "start" of a run was based on setpoint increases and kiln temperature increases. We now have mostly clean plots with a few exceptions.  

## Assorted

Assorted lots from each kiln.  

```{r}
all_kilns <- bind_rows(
  kilns_AB %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_C  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_D  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_E  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_F  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_G  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_H  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln)
)

# random sample of LOTNOs
set.seed(505)
n_kilns <- sample_n(all_kilns, 16) %>% dplyr::select(LOTNO) %>% unlist()

n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "A"), 2) %>% dplyr::select(LOTNO) %>% unlist()
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "B"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "C"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "D"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "E"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "F"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "G"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "H"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- unlist(n_kilns)

sample_kilns <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns, lot_compare=T)
```

## A

```{r}
# random sample of LOTNOs
set.seed(76)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "A"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_a <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_a)
```

## B

```{r}
# random sample of LOTNOs
set.seed(76)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "B"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_b <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_b)
```

## C

```{r}
# random sample of LOTNOs
set.seed(76)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "C"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_c <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_c)
```

## D

```{r}
# random sample of LOTNOs
set.seed(15)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "D"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_d <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_d)
```

## E

```{r}
# random sample of LOTNOs
set.seed(76)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "E"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_e <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_e)
```

## F

```{r}
# random sample of LOTNOs
set.seed(15)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "F"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_f <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_f)
```

## G

```{r}
# random sample of LOTNOs
set.seed(15)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "G"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_g <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_g)
```

## H

```{r}
# random sample of LOTNOs
set.seed(15)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "H"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_h <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_h)
```


# AUC Calculations {.tabset}

One measure mentioned to have potential importance in defect rate is variation between **setpoint** and **average kiln temperature** in the 400°C to 600°C range. An algorithm takes the absolute value of the difference between the values, and adds them together to produce a new feature, displayed below.    

## AUC

Base plot of temperature and setpoint over time, with green area representing the claculated area between the two curves. Numeric values also printed for comparison.  

```{r}
plotAucValues(sample_kilns, x.nudge = 900, y.nudge = 0)
```

## Cropped

```{r}
plotAucValues(sample_kilns, crop=T, x.nudge = 0, y.nudge = 200)
```

## Cropped, unlabeled

```{r}
plotAucValues(sample_kilns, crop=T, free.x=T)
```







# AUC Analysis {.tabset}

## Boxplot

As could be seen in the above plots, some kilns exhibit far more variation than others. The below boxplot shows the kilns G and H have by far the most consistent operation.  

```{r}
df_merged_auc %>% 
  group_by(LOTNO) %>% slice(1) %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  # ggplot(aes(x=aucDiff, y=fct_reorder(KILN,aucDiff), fill =KILN2))+
  ggplot(aes(x=aucDiff, y=fct_reorder(KILN2,aucDiff)))+
  geom_boxplot(outlier.alpha = 0,
               outlier.shape = 21)+
  geom_jitter(height = .2, alpha=.1)+
  labs(title = "Setpoint vs temperature variation between kilns")+
  xlab("Area between curves")+
  ylab("Kiln")+
  theme(legend.position = 'none')+
  scale_x_continuous(labels = scales::label_number())
```

## Density

Most of the distributions are not distributed normally.

```{r}
df_yields_auc %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  ggplot(aes(x=aucDiff, y = ..count../sum(..count..)))+
  geom_density()+
  scale_y_continuous(labels = scales::percent_format())+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  facet_wrap(~KILN2, scales='free')
  # facet_wrap(~KILN2)

```

