---
title: "Kiln Data"
author: "Edward Yu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: paper
    highlight: textmate
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo    = TRUE,
                      error   = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      cache   = TRUE,
                      fig.width = 8, fig.height = 6,
                      dpi = 180)
rm(list = ls())

# load stuff
library(tidyverse)
library(plotly)
library(ggpointdensity)
library(viridis)
library(magrittr)
library(knitr)
library(kableExtra)

theme_set(theme_minimal())

source("../src/kilnFunctions.R")
source("../src/userFunctions.R")

# import data -------------------------------------------------------------
df_merged    <- read_csv("../data/processed_data/df_merged.csv")
df_yields    <- read_csv("../data/processed_data/df_yields.csv")
df_defects   <- read_csv("../data/processed_data/df_defects.csv")
kilns_AB  <- read_csv("../data/processed_data/kilns_AB.csv") %>% mutate_if(is.character,as.factor)
kilns_C   <- read_csv("../data/processed_data/kilns_C.csv")  %>% mutate_if(is.character,as.factor)
kilns_D   <- read_csv("../data/processed_data/kilns_D.csv")  %>% mutate_if(is.character,as.factor)
kilns_E   <- read_csv("../data/processed_data/kilns_E.csv")  %>% mutate_if(is.character,as.factor)
kilns_F   <- read_csv("../data/processed_data/kilns_F.csv")  %>% 
  mutate_if(is.character,as.factor) %>% 
  mutate(kiln = as.factor("F"))
kilns_G   <- read_csv("../data/processed_data/kilns_G.csv")  %>% mutate_if(is.character,as.factor)
kilns_H   <- read_csv("../data/processed_data/kilns_H.csv")  %>% mutate_if(is.character,as.factor)

allAucValues <- read_csv("../data/processed_data/kilnsAucValues.csv")

# join kiln AUC to original data ------------------------------------------
df_merged_auc <- df_merged %>% 
  left_join(allAucValues, by='LOTNO') %>% 
  dplyr::mutate_if(is.character, as.factor) %>% 
  mutate(LOTNO = as.factor(LOTNO),
         ITEM = as.factor(ITEM)) %>%
  na.omit(aucDiff)

df_yields_auc <- df_yields %>% 
  left_join(allAucValues, by='LOTNO') %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(LOTNO = as.factor(LOTNO),
         ITEM = as.factor(ITEM)) %>% 
  mutate(LOTNO = as.factor(LOTNO))%>% 
  na.omit(aucDiff)

df_defects_auc <- df_defects %>% 
  left_join(allAucValues, by='LOTNO') %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(LOTNO = as.factor(LOTNO),
         ITEM = as.factor(ITEM)) %>% 
  mutate(LOTNO = as.factor(LOTNO))%>% 
  na.omit(aucDiff)
```

# Cleaned data {.tabset .tabset-pills .tabset-fade}

Imported and cleaned all kiln data available from 2018-2020. Involved using an algorithm to remove high peaks and valleys, detection of when the "start" of a run was based on setpoint increases and kiln temperature increases. We now have mostly clean plots with a few exceptions.  

## Assorted

Assorted lots from each kiln.  

```{r}
all_kilns <- bind_rows(
  kilns_AB %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_C  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_D  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_E  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_F  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_G  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln),
  kilns_H  %>% dplyr::select(time, setpoint, avg_kiln_temp, LOTNO, auc_min, auc_max, kiln)
)

# random sample of LOTNOs
set.seed(505)
n_kilns <- sample_n(all_kilns, 16) %>% dplyr::select(LOTNO) %>% unlist()

n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "A"), 2) %>% dplyr::select(LOTNO) %>% unlist()
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "B"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "C"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "D"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "E"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "F"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "G"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- bind_rows(sample_n(all_kilns %>% dplyr::filter(kiln == "H"), 2) %>% dplyr::select(LOTNO) %>% unlist(), n_kilns)
n_kilns <- unlist(n_kilns)

sample_kilns <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns, lot_compare=T)
```

## A

```{r}
# random sample of LOTNOs
set.seed(76)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "A"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_a <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_a)
```

## B

```{r}
# random sample of LOTNOs
set.seed(76)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "B"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_b <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_b)
```

## C

```{r}
# random sample of LOTNOs
set.seed(76)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "C"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_c <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_c)
```

## D

```{r}
# random sample of LOTNOs
set.seed(15)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "D"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_d <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_d)
```

## E

```{r}
# random sample of LOTNOs
set.seed(76)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "E"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_e <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_e)
```

## F

```{r}
# random sample of LOTNOs
set.seed(15)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "F"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_f <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_f)
```

## G

```{r}
# random sample of LOTNOs
set.seed(15)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "G"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_g <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_g)
```

## H

```{r}
# random sample of LOTNOs
set.seed(15)
n_kilns <- sample_n(all_kilns %>% dplyr::filter(kiln == "H"), 16) %>% dplyr::select(LOTNO) %>% unlist()

sample_kilns_h <- all_kilns %>% 
  dplyr::filter(LOTNO %in% n_kilns) %>% 
  mutate(LOTNO = as.character(LOTNO)) %>% 
  mutate(LOTNO = factor(LOTNO)) %>% 
  mutateAucValues()

plot_range(sample_kilns_h)
```


# AUC Calculations {.tabset .tabset-pills .tabset-fade}

One measure mentioned to have potential importance in defect rate is variation between **setpoint** and **average kiln temperature** in the 400°C to 600°C range. An algorithm takes the absolute value of the difference between the values, and adds them together to produce a new feature, displayed below.    

## AUC

Base plot of temperature and setpoint over time, with green area representing the claculated area between the two curves. Numeric values also printed for comparison.  

```{r}
plotAucValues(sample_kilns, x.nudge = 900, y.nudge = 0)
```

## Cropped

```{r}
plotAucValues(sample_kilns, crop=T, x.nudge = 0, y.nudge = 200)
```

## Cropped, unlabeled

```{r}
plotAucValues(sample_kilns, crop=T, free.x=T)
```







# AUC distribution {.tabset .tabset-pills .tabset-fade}

Distribution varies greatly between kilns

## Boxplot

Kilns G and H have by far the most consistent operation based on our measure.  

```{r}
df_merged_auc %>% 
  group_by(LOTNO) %>% slice(1) %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  # ggplot(aes(x=aucDiff, y=fct_reorder(KILN,aucDiff), fill =KILN2))+
  ggplot(aes(x=aucDiff, y=fct_reorder(KILN2,aucDiff)))+
  geom_boxplot(outlier.alpha = 0,
               outlier.shape = 21)+
  geom_jitter(height = .2, alpha=.1)+
  labs(title = "Setpoint vs temperature variation between kilns")+
  xlab("Area between curves")+
  ylab("Kiln")+
  theme(legend.position = 'none')+
  scale_x_continuous(labels = scales::label_number())
```

## Density

Most of the distributions are not distributed normally and potentially require transformation depending on the analysis performed.  

```{r}
df_yields_auc %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  ggplot(aes(x=aucDiff, y = ..count../sum(..count..)))+
  geom_density()+
  scale_y_continuous(labels = scales::percent_format())+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  facet_wrap(~KILN2, scales='free')
  # facet_wrap(~KILN2)

```

# Impact on yields

How does our new area between the curves feature relate to yield values?  

## Lot yields  {.tabset .tabset-pills .tabset-fade}

Starting very broadly, there are very weak correlations between the AUC feature and overall lot yields.  

### All 

```{r}
# join correlation of AUC, lot yield to original DF and plot
df <- df_yields_auc %>% 
  group_by(LOTNO, KILN, aucDiff, temp_avg, precip, snow_fall, snow_depth) %>% 
  dplyr::summarise(
    total_fired = sum(TOTAL_ITEM_FIRED),
    total_rejected = sum(TOTAL_ITEM_REJECTED),
    pct_lot_yield = (total_fired - total_rejected) / total_fired
  ) %>% 
  mutate(KILN2 = str_replace(KILN, "R", ""))

df <- df %>% 
  group_by(KILN2) %>% 
  dplyr::summarise(cor = cor(pct_lot_yield, aucDiff)) %>% 
  left_join(df) %>% 
  mutate(kiln_cor = factor(paste0(KILN2, " (", round(cor,3), ")")))

df %>% 
  ggplot(aes(x=aucDiff, y=pct_lot_yield))+
  # ggplot(aes(x=pct_lot_yield, y=aucDiff))+
  geom_pointdensity(alpha=.8, size=1)+
  scale_x_continuous(limits = c(0,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  facet_wrap(~kiln_cor, scales='free_y')+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus entire lot yields',
       subtitle = 'Correlation value (in parentheses)')+
  theme(legend.position = 'none')


df %>% count(cor, KILN2) %>%  
  arrange(-abs(cor)) %>% 
  mutate(
    cor = cell_spec(round(cor,2), 'html', color= ifelse(cor < 0, 'red', 'black'))
         ) %>% 
  set_colnames(c("Correlation", "Kiln", "Observations")) %>% 
  kable(format = 'html', escape = 'F') %>% 
  kable_styling('striped',full_width = F)
```

### Trendline

Trendline added.  

```{r}
df %>% 
  # ggplot(aes(x=pct_lot_yield, y=aucDiff))+
  ggplot(aes(x=aucDiff, y=pct_lot_yield))+
  geom_pointdensity(alpha=.8, size=1)+
  geom_smooth(alpha=.1, color = 'red')+
  scale_x_continuous(limits = c(0,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  facet_wrap(~kiln_cor, scales='free_y')+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus entire lot yields',
       subtitle = 'Correlation value (in parentheses)')+
  theme(legend.position = 'none')
```

### Cropped

Cropped the x-axis: 80 - 100%

```{r}
# join correlation of AUC, lot yield to original DF and plot
df <- df_yields_auc %>% 
  group_by(LOTNO, KILN, aucDiff, temp_avg, precip, snow_fall, snow_depth) %>% 
  dplyr::summarise(
    total_fired = sum(TOTAL_ITEM_FIRED),
    total_rejected = sum(TOTAL_ITEM_REJECTED),
    pct_lot_yield = (total_fired - total_rejected) / total_fired
  ) %>% 
  mutate(KILN2 = str_replace(KILN, "R", ""))

df <- df %>% 
  group_by(KILN2) %>% 
  dplyr::summarise(cor = cor(pct_lot_yield, aucDiff)) %>% 
  left_join(df) %>% 
  mutate(kiln_cor = factor(paste0(KILN2, " (", round(cor,3), ")")))

df %>% 
  # ggplot(aes(x=pct_lot_yield, y=aucDiff))+
  ggplot(aes(x=aucDiff, y=pct_lot_yield))+
  geom_pointdensity(alpha=.8, size=1)+
  scale_x_continuous(limits = c(0.8,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  facet_wrap(~kiln_cor, scales='free_y')+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus entire lot yields',
       subtitle = 'Correlation value (in parentheses)')+
  theme(legend.position = 'none')
```

## Item yields {.tabset .tabset-pills .tabset-fade}

Above, we tested the idea that yields of an entire lot could be affected by our AUC feature. Next, we hone in on specific kilns and determine if different `items` might show different yields within the kiln.  

### A

```{r}
# yields df of kiln
df <- df_yields_auc %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  dplyr::filter(KILN2 == "A")

# get top items fired in kiln
df_items <- df %>% 
  count(DESCRIPTION) %>% 
  arrange(-n) %>% 
  slice(1:9)

# filter original df for top items
df <- df %>% 
  dplyr::filter(DESCRIPTION %in% df_items$DESCRIPTION)

# get cor values and join to original
# df$DESCRIPTION <- gsub('[[:punct:]]', "", df$DESCRIPTION)
df_cor <- df %>% 
  group_by(DESCRIPTION) %>% 
  dplyr::summarise(cor = round(cor(aucDiff, total_item_pct_yield),2)) %>%
  left_join(df) %>% 
  dplyr::select(DESCRIPTION, cor) %>% 
  group_by(DESCRIPTION) %>% slice(1)

df <- df %>% 
  left_join(df_cor) %>% 
  mutate(descr_cor = paste0(DESCRIPTION, " (", cor, ")")) %>% 
  right_join(df)

# plot
df %>% 
  ggplot(aes(x=aucDiff, y=total_item_pct_yield))+
  # geom_point()+
  # geom_bin2d()+
  # stat_density_2d(aes(fill=..level..))+
  # stat_bin_hex()+
  geom_pointdensity()+
  scale_x_continuous(limits = c(0,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus item yields')+
  # facet_wrap(~descr_cor)+
  facet_wrap(~descr_cor, scales='free_y')+
  theme(legend.position = 'none')

# table
df %>% 
  count(cor, DESCRIPTION) %>% 
  arrange(-abs(cor)) %>% 
  mutate(
    cor = cell_spec(round(cor,2), 'html', color= ifelse(cor < 0, 'red', 'black'))
  ) %>% 
  set_colnames(c("Correlation", "Description", "Observations")) %>% 
  kable(format = 'html', escape = 'F') %>% 
  kable_styling('striped',full_width = F)
```

### B

```{r}
# yields df of kiln
df <- df_yields_auc %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  dplyr::filter(KILN2 == "B")

# get top items fired in kiln
df_items <- df %>% 
  count(DESCRIPTION) %>% 
  arrange(-n) %>% 
  slice(1:9)

# filter original df for top items
df <- df %>% 
  dplyr::filter(DESCRIPTION %in% df_items$DESCRIPTION)

# get cor values and join to original
# df$DESCRIPTION <- gsub('[[:punct:]]', "", df$DESCRIPTION)
df_cor <- df %>% 
  group_by(DESCRIPTION) %>% 
  dplyr::summarise(cor = round(cor(aucDiff, total_item_pct_yield),2)) %>%
  left_join(df) %>% 
  dplyr::select(DESCRIPTION, cor) %>% 
  group_by(DESCRIPTION) %>% slice(1)

df <- df %>% 
  left_join(df_cor) %>% 
  mutate(descr_cor = paste0(DESCRIPTION, " (", cor, ")")) %>% 
  right_join(df)

# plot
df %>% 
  ggplot(aes(x=aucDiff, y=total_item_pct_yield))+
  # geom_point()+
  # geom_bin2d()+
  # stat_density_2d(aes(fill=..level..))+
  # stat_bin_hex()+
  geom_pointdensity()+
  scale_x_continuous(limits = c(0,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus item yields')+
  # facet_wrap(~descr_cor)+
  facet_wrap(~descr_cor, scales='free_y')+
  theme(legend.position = 'none')

# table
df %>% 
  count(cor, DESCRIPTION) %>% 
  arrange(-abs(cor)) %>% 
  mutate(
    cor = cell_spec(round(cor,2), 'html', color= ifelse(cor < 0, 'red', 'black'))
  ) %>% 
  set_colnames(c("Correlation", "Description", "Observations")) %>% 
  kable(format = 'html', escape = 'F') %>% 
  kable_styling('striped',full_width = F)

```

### C

```{r}
# yields df of kiln
df <- df_yields_auc %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  dplyr::filter(KILN2 == "C")

# get top items fired in kiln
df_items <- df %>% 
  count(DESCRIPTION) %>% 
  arrange(-n) %>% 
  slice(1:9)

# filter original df for top items
df <- df %>% 
  dplyr::filter(DESCRIPTION %in% df_items$DESCRIPTION)

# get cor values and join to original
# df$DESCRIPTION <- gsub('[[:punct:]]', "", df$DESCRIPTION)
df_cor <- df %>% 
  group_by(DESCRIPTION) %>% 
  dplyr::summarise(cor = round(cor(aucDiff, total_item_pct_yield),2)) %>%
  left_join(df) %>% 
  dplyr::select(DESCRIPTION, cor) %>% 
  group_by(DESCRIPTION) %>% slice(1)

df <- df %>% 
  left_join(df_cor) %>% 
  mutate(descr_cor = paste0(DESCRIPTION, " (", cor, ")")) %>% 
  right_join(df)

# plot
df %>% 
  ggplot(aes(x=aucDiff, y=total_item_pct_yield))+
  # geom_point()+
  # geom_bin2d()+
  # stat_density_2d(aes(fill=..level..))+
  # stat_bin_hex()+
  geom_pointdensity()+
  scale_x_continuous(limits = c(0,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus item yields')+
  # facet_wrap(~descr_cor)+
  facet_wrap(~descr_cor, scales='free_y')+
  theme(legend.position = 'none')

# table
df %>% 
  count(cor, DESCRIPTION) %>% 
  arrange(-abs(cor)) %>% 
  mutate(
    cor = cell_spec(round(cor,2), 'html', color= ifelse(cor < 0, 'red', 'black'))
  ) %>% 
  set_colnames(c("Correlation", "Description", "Observations")) %>% 
  kable(format = 'html', escape = 'F') %>% 
  kable_styling('striped',full_width = F)

```

### D

```{r}
# yields df of kiln
df <- df_yields_auc %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  dplyr::filter(KILN2 == "D")

# get top items fired in kiln
df_items <- df %>% 
  count(DESCRIPTION) %>% 
  arrange(-n) %>% 
  slice(1:9)

# filter original df for top items
df <- df %>% 
  dplyr::filter(DESCRIPTION %in% df_items$DESCRIPTION)

# get cor values and join to original
# df$DESCRIPTION <- gsub('[[:punct:]]', "", df$DESCRIPTION)
df_cor <- df %>% 
  group_by(DESCRIPTION) %>% 
  dplyr::summarise(cor = round(cor(aucDiff, total_item_pct_yield),2)) %>%
  left_join(df) %>% 
  dplyr::select(DESCRIPTION, cor) %>% 
  group_by(DESCRIPTION) %>% slice(1)

df <- df %>% 
  left_join(df_cor) %>% 
  mutate(descr_cor = paste0(DESCRIPTION, " (", cor, ")")) %>% 
  right_join(df)

# plot
df %>% 
  ggplot(aes(x=aucDiff, y=total_item_pct_yield))+
  # geom_point()+
  # geom_bin2d()+
  # stat_density_2d(aes(fill=..level..))+
  # stat_bin_hex()+
  geom_pointdensity()+
  scale_x_continuous(limits = c(0,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus item yields')+
  # facet_wrap(~descr_cor)+
  facet_wrap(~descr_cor, scales='free_y')+
  theme(legend.position = 'none')

# table
df %>% 
  count(cor, DESCRIPTION) %>% 
  arrange(-abs(cor)) %>% 
  mutate(
    cor = cell_spec(round(cor,2), 'html', color= ifelse(cor < 0, 'red', 'black'))
  ) %>% 
  set_colnames(c("Correlation", "Description", "Observations")) %>% 
  kable(format = 'html', escape = 'F') %>% 
  kable_styling('striped',full_width = F)

```

### E

```{r}
# yields df of kiln
df <- df_yields_auc %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  dplyr::filter(KILN2 == "E")

# get top items fired in kiln
df_items <- df %>% 
  count(DESCRIPTION) %>% 
  arrange(-n) %>% 
  slice(1:9)

# filter original df for top items
df <- df %>% 
  dplyr::filter(DESCRIPTION %in% df_items$DESCRIPTION)

# get cor values and join to original
# df$DESCRIPTION <- gsub('[[:punct:]]', "", df$DESCRIPTION)
df_cor <- df %>% 
  group_by(DESCRIPTION) %>% 
  dplyr::summarise(cor = round(cor(aucDiff, total_item_pct_yield),2)) %>%
  left_join(df) %>% 
  dplyr::select(DESCRIPTION, cor) %>% 
  group_by(DESCRIPTION) %>% slice(1)

df <- df %>% 
  left_join(df_cor) %>% 
  mutate(descr_cor = paste0(DESCRIPTION, " (", cor, ")")) %>% 
  right_join(df)

# plot
df %>% 
  ggplot(aes(x=aucDiff, y=total_item_pct_yield))+
  # geom_point()+
  # geom_bin2d()+
  # stat_density_2d(aes(fill=..level..))+
  # stat_bin_hex()+
  geom_pointdensity()+
  scale_x_continuous(limits = c(0,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus item yields')+
  # facet_wrap(~descr_cor)+
  facet_wrap(~descr_cor, scales='free_y')+
  theme(legend.position = 'none')

# table
df %>% 
  count(cor, DESCRIPTION) %>% 
  arrange(-abs(cor)) %>% 
  mutate(
    cor = cell_spec(round(cor,2), 'html', color= ifelse(cor < 0, 'red', 'black'))
  ) %>% 
  set_colnames(c("Correlation", "Description", "Observations")) %>% 
  kable(format = 'html', escape = 'F') %>% 
  kable_styling('striped',full_width = F)

```

### F

```{r}
# yields df of kiln
df <- df_yields_auc %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  dplyr::filter(KILN2 == "F")

# get top items fired in kiln
df_items <- df %>% 
  count(DESCRIPTION) %>% 
  arrange(-n) %>% 
  slice(1:9)

# filter original df for top items
df <- df %>% 
  dplyr::filter(DESCRIPTION %in% df_items$DESCRIPTION)

# get cor values and join to original
# df$DESCRIPTION <- gsub('[[:punct:]]', "", df$DESCRIPTION)
df_cor <- df %>% 
  group_by(DESCRIPTION) %>% 
  dplyr::summarise(cor = round(cor(aucDiff, total_item_pct_yield),2)) %>%
  left_join(df) %>% 
  dplyr::select(DESCRIPTION, cor) %>% 
  group_by(DESCRIPTION) %>% slice(1)

df <- df %>% 
  left_join(df_cor) %>% 
  mutate(descr_cor = paste0(DESCRIPTION, " (", cor, ")")) %>% 
  right_join(df)

# plot
df %>% 
  ggplot(aes(x=aucDiff, y=total_item_pct_yield))+
  # geom_point()+
  # geom_bin2d()+
  # stat_density_2d(aes(fill=..level..))+
  # stat_bin_hex()+
  geom_pointdensity()+
  scale_x_continuous(limits = c(0,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus item yields')+
  # facet_wrap(~descr_cor)+
  facet_wrap(~descr_cor, scales='free_y')+
  theme(legend.position = 'none')

# table
df %>% 
  count(cor, DESCRIPTION) %>% 
  arrange(-abs(cor)) %>% 
  mutate(
    cor = cell_spec(round(cor,2), 'html', color= ifelse(cor < 0, 'red', 'black'))
  ) %>% 
  set_colnames(c("Correlation", "Description", "Observations")) %>% 
  kable(format = 'html', escape = 'F') %>% 
  kable_styling('striped',full_width = F)

```

### G

```{r}
# yields df of kiln
df <- df_yields_auc %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  dplyr::filter(KILN2 == "G")

# get top items fired in kiln
df_items <- df %>% 
  count(DESCRIPTION) %>% 
  arrange(-n) %>% 
  slice(1:9)

# filter original df for top items
df <- df %>% 
  dplyr::filter(DESCRIPTION %in% df_items$DESCRIPTION)

# get cor values and join to original
# df$DESCRIPTION <- gsub('[[:punct:]]', "", df$DESCRIPTION)
df_cor <- df %>% 
  group_by(DESCRIPTION) %>% 
  dplyr::summarise(cor = round(cor(aucDiff, total_item_pct_yield),2)) %>%
  left_join(df) %>% 
  dplyr::select(DESCRIPTION, cor) %>% 
  group_by(DESCRIPTION) %>% slice(1)

df <- df %>% 
  left_join(df_cor) %>% 
  mutate(descr_cor = paste0(DESCRIPTION, " (", cor, ")")) %>% 
  right_join(df)

# plot
df %>% 
  ggplot(aes(x=aucDiff, y=total_item_pct_yield))+
  # geom_point()+
  # geom_bin2d()+
  # stat_density_2d(aes(fill=..level..))+
  # stat_bin_hex()+
  geom_pointdensity()+
  scale_x_continuous(limits = c(0,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus item yields')+
  # facet_wrap(~descr_cor)+
  facet_wrap(~descr_cor, scales='free_y')+
  theme(legend.position = 'none')

# table
df %>% 
  count(cor, DESCRIPTION) %>% 
  arrange(-abs(cor)) %>% 
  mutate(
    cor = cell_spec(round(cor,2), 'html', color= ifelse(cor < 0, 'red', 'black'))
  ) %>% 
  set_colnames(c("Correlation", "Description", "Observations")) %>% 
  kable(format = 'html', escape = 'F') %>% 
  kable_styling('striped',full_width = F)

```

### H

```{r}
# yields df of kiln
df <- df_yields_auc %>% 
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  dplyr::filter(KILN2 == "H")

# get top items fired in kiln
df_items <- df %>% 
  count(DESCRIPTION) %>% 
  arrange(-n) %>% 
  slice(1:9)

# filter original df for top items
df <- df %>% 
  dplyr::filter(DESCRIPTION %in% df_items$DESCRIPTION)

# get cor values and join to original
# df$DESCRIPTION <- gsub('[[:punct:]]', "", df$DESCRIPTION)
df_cor <- df %>% 
  group_by(DESCRIPTION) %>% 
  dplyr::summarise(cor = round(cor(aucDiff, total_item_pct_yield),2)) %>%
  left_join(df) %>% 
  dplyr::select(DESCRIPTION, cor) %>% 
  group_by(DESCRIPTION) %>% slice(1)

df <- df %>% 
  left_join(df_cor) %>% 
  mutate(descr_cor = paste0(DESCRIPTION, " (", cor, ")")) %>% 
  right_join(df)

# plot
df %>% 
  ggplot(aes(x=aucDiff, y=total_item_pct_yield))+
  # geom_point()+
  # geom_bin2d()+
  # stat_density_2d(aes(fill=..level..))+
  # stat_bin_hex()+
  geom_pointdensity()+
  scale_x_continuous(limits = c(0,1),labels = scales::percent_format())+
  scale_y_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_color_viridis_c()+
  xlab('Lot yield')+
  ylab('Area between curves')+
  labs(title = 'AUC versus item yields')+
  # facet_wrap(~descr_cor)+
  facet_wrap(~descr_cor, scales='free_y')+
  theme(legend.position = 'none')

# table
df %>% 
  count(cor, DESCRIPTION) %>% 
  arrange(-abs(cor)) %>% 
  mutate(
    cor = cell_spec(round(cor,2), 'html', color= ifelse(cor < 0, 'red', 'black'))
  ) %>% 
  set_colnames(c("Correlation", "Description", "Observations")) %>% 
  kable(format = 'html', escape = 'F') %>% 
  kable_styling('striped',full_width = F)

```

# Defect rates by defect cause {.tabset .tabset-pills .tabset-fade}

## CW

Does AUC effect the occurrence of cracked webs of an item, on a per lot, per kiln basis (remember we cannot compare kilns to one another at this point due to the varying value distributions between them)?

```{r}
# get lot fired total
df <- df_merged_auc %>%
  # lump kilns
  mutate(KILN2 = str_replace(KILN, "R", "")) %>% 
  mutate(reject_count_single_row = reject_vol_single_row_D * vol_piece) %>% 
  group_by(LOTNO) %>% 
  dplyr::summarise(total_lot_count_fired = sum(total_item_count_fired_D)) %>% 
  right_join(df_merged_auc)

# get defects total
df <- df %>% 
  group_by(LOTNO, CAUSE) %>%
  dplyr::summarise(total_defect_count_per_lot = sum(total_item_count_rejected_D)) %>% 
  right_join(df) %>% 
  group_by(LOTNO, CAUSE) %>%
  slice(1) %>% ungroup() %>%
  dplyr::select(LOTNO, CAUSE, total_lot_count_fired, total_defect_count_per_lot, aucDiff) %>% 
  mutate(pct_defect = 1 - (total_lot_count_fired - total_defect_count_per_lot)  / total_lot_count_fired )
  
# fill missing values
pct_defect_by_lot <- df %>% 
  pivot_wider(id_cols     = LOTNO, 
              names_from  = CAUSE, 
              values_from = pct_defect,
              values_fill = 0)

# join pct defect to aucDiff
pct_defect_by_lot <- pct_defect_by_lot %>% 
  pivot_longer(cols = BE:BIT) %>% 
  # join to aucDiff 
  left_join(
    df_merged_auc %>% 
      mutate(KILN = str_replace(KILN, "R", "")) %>% 
      group_by(LOTNO) %>% slice(1) %>% 
      dplyr::select(LOTNO, KILN, aucDiff)
  ) %>% 
  set_colnames(c("LOTNO", "CAUSE", "defect_pct", "KILN", "aucDiff")) %>% 
  mutate_if(is.character, factor)

# for CW, what is the relationship between KILN and aucDiff?
def = "CW"

pct_defect_by_lot %>%
  dplyr::filter(CAUSE == def) %>% 
  group_by(KILN) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(CAUSE == def)) %>% 
  dplyr::mutate(kiln_cor = paste0(KILN, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity()+
  scale_color_viridis_c()+
  facet_wrap(~kiln_cor,scales='free_x')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,.15))+
  labs(
    title = paste0(def, " defect rate per lot vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0(def, " defect rate"))+
  theme(legend.position = 'none')
```

## BE

```{r}
def = "BE"

pct_defect_by_lot %>%
  dplyr::filter(CAUSE == def) %>% 
  group_by(KILN) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(CAUSE == def)) %>% 
  dplyr::mutate(kiln_cor = paste0(KILN, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity()+
  scale_color_viridis_c()+
  facet_wrap(~kiln_cor,scales='free_x')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,.2))+
  labs(
    title = paste0(def, " defect rate per lot vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0(def, " defect rate"))+
  theme(legend.position = 'none')

```

## DC

```{r}
def = "DC"

pct_defect_by_lot %>%
  dplyr::filter(CAUSE == def) %>% 
  group_by(KILN) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(CAUSE == def)) %>% 
  dplyr::mutate(kiln_cor = paste0(KILN, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity()+
  scale_color_viridis_c()+
  facet_wrap(~kiln_cor, scales = 'free')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format(), limits = c(0,.1))+
  labs(
    title = paste0(def, " defect rate per lot vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0(def, " defect rate"))+
  theme(legend.position = 'none')

```

# Defect rates by kiln {.tabset .tabset-pills .tabset-fade}

## A

```{r}
# for each kiln, compare the defect rate vs AUC for each cause
kil = "A"

pct_defect_by_lot %>%
  dplyr::filter(KILN == kil) %>% 
  group_by(CAUSE) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff),
                   cor = ifelse(is.na(cor), 0, cor)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(KILN == kil)) %>% 
  dplyr::mutate(cause_cor = paste0(CAUSE, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity(adjust = .2)+
  scale_color_viridis_c()+
  facet_wrap(~cause_cor, scales='free')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format())+
  # scale_y_continuous(labels = scales::percent_format(), limits = c(0,.06))+
  labs(
    title = paste0("Kiln ", kil, " defect rate per defect vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0("Defect rate"))+
  theme(legend.position = 'none')

```

## B

```{r}
# for each kiln, compare the defect rate vs AUC for each cause
kil = "B"

pct_defect_by_lot %>%
  dplyr::filter(KILN == kil) %>% 
  group_by(CAUSE) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff),
                   cor = ifelse(is.na(cor), 0, cor)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(KILN == kil)) %>% 
  dplyr::mutate(cause_cor = paste0(CAUSE, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity(adjust = .2)+
  scale_color_viridis_c()+
  facet_wrap(~cause_cor, scales='free')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format())+
  # scale_y_continuous(labels = scales::percent_format(), limits = c(0,.06))+
  labs(
    title = paste0("Kiln ", kil, " defect rate per defect vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0("Defect rate"))+
  theme(legend.position = 'none')

```

## C

```{r}
# for each kiln, compare the defect rate vs AUC for each cause
kil = "C"

pct_defect_by_lot %>%
  dplyr::filter(KILN == kil) %>% 
  group_by(CAUSE) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff),
                   cor = ifelse(is.na(cor), 0, cor)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(KILN == kil)) %>% 
  dplyr::mutate(cause_cor = paste0(CAUSE, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity(adjust = .2)+
  scale_color_viridis_c()+
  facet_wrap(~cause_cor, scales='free')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format())+
  # scale_y_continuous(labels = scales::percent_format(), limits = c(0,.06))+
  labs(
    title = paste0("Kiln ", kil, " defect rate per defect vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0("Defect rate"))+
  theme(legend.position = 'none')

```

## D

```{r}
# for each kiln, compare the defect rate vs AUC for each cause
kil = "D"

pct_defect_by_lot %>%
  dplyr::filter(KILN == kil) %>% 
  group_by(CAUSE) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff),
                   cor = ifelse(is.na(cor), 0, cor)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(KILN == kil)) %>% 
  dplyr::mutate(cause_cor = paste0(CAUSE, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity(adjust = .2)+
  scale_color_viridis_c()+
  facet_wrap(~cause_cor, scales='free')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format())+
  # scale_y_continuous(labels = scales::percent_format(), limits = c(0,.06))+
  labs(
    title = paste0("Kiln ", kil, " defect rate per defect vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0("Defect rate"))+
  theme(legend.position = 'none')

```

## E

```{r}
# for each kiln, compare the defect rate vs AUC for each cause
kil = "E"

pct_defect_by_lot %>%
  dplyr::filter(KILN == kil) %>% 
  group_by(CAUSE) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff),
                   cor = ifelse(is.na(cor), 0, cor)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(KILN == kil)) %>% 
  dplyr::mutate(cause_cor = paste0(CAUSE, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity(adjust = .2)+
  scale_color_viridis_c()+
  facet_wrap(~cause_cor, scales='free')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format())+
  # scale_y_continuous(labels = scales::percent_format(), limits = c(0,.06))+
  labs(
    title = paste0("Kiln ", kil, " defect rate per defect vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0("Defect rate"))+
  theme(legend.position = 'none')

```

## F

```{r}
# for each kiln, compare the defect rate vs AUC for each cause
kil = "F"

pct_defect_by_lot %>%
  dplyr::filter(KILN == kil) %>% 
  group_by(CAUSE) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff),
                   cor = ifelse(is.na(cor), 0, cor)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(KILN == kil)) %>% 
  dplyr::mutate(cause_cor = paste0(CAUSE, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity(adjust = .2)+
  scale_color_viridis_c()+
  facet_wrap(~cause_cor, scales='free')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format())+
  # scale_y_continuous(labels = scales::percent_format(), limits = c(0,.06))+
  labs(
    title = paste0("Kiln ", kil, " defect rate per defect vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0("Defect rate"))+
  theme(legend.position = 'none')

```

## G

```{r}
# for each kiln, compare the defect rate vs AUC for each cause
kil = "G"

pct_defect_by_lot %>%
  dplyr::filter(KILN == kil) %>% 
  group_by(CAUSE) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff),
                   cor = ifelse(is.na(cor), 0, cor)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(KILN == kil)) %>% 
  dplyr::mutate(cause_cor = paste0(CAUSE, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity(adjust = .2)+
  scale_color_viridis_c()+
  facet_wrap(~cause_cor, scales='free')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format())+
  # scale_y_continuous(labels = scales::percent_format(), limits = c(0,.06))+
  labs(
    title = paste0("Kiln ", kil, " defect rate per defect vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0("Defect rate"))+
  theme(legend.position = 'none')

```

## H

```{r}
# for each kiln, compare the defect rate vs AUC for each cause
kil = "H"

pct_defect_by_lot %>%
  dplyr::filter(KILN == kil) %>% 
  group_by(CAUSE) %>%
  dplyr::summarise(cor = cor(defect_pct, aucDiff),
                   cor = ifelse(is.na(cor), 0, cor)) %>%
  # arrange(-cor) %>%
  right_join(pct_defect_by_lot %>%
               dplyr::filter(KILN == kil)) %>% 
  dplyr::mutate(cause_cor = paste0(CAUSE, " (", round(cor,2), ")")) %>%
  ggplot(aes(y=defect_pct, x=aucDiff))+
  geom_smooth(alpha=.2)+
  geom_pointdensity(adjust = .2)+
  scale_color_viridis_c()+
  facet_wrap(~cause_cor, scales='free')+
  scale_x_continuous(labels = scales::number_format(scale=1e-3, suffix='K'))+
  scale_y_continuous(labels = scales::percent_format())+
  # scale_y_continuous(labels = scales::percent_format(), limits = c(0,.06))+
  labs(
    title = paste0("Kiln ", kil, " defect rate per defect vs AUC"),
    subtitle = "Correlation value (in parentheses)"
  )+
  xlab("Area between setpoint, kiln temp")+
  ylab(paste0("Defect rate"))+
  theme(legend.position = 'none')

```
