---
title: "Kiln Pressure Data"
author: "Edward Yu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: paper
    highlight: textmate
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo    = TRUE,
                      error   = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      cache   = TRUE,
                      fig.width = 8, fig.height = 8,
                      dpi = 180)
rm(list = ls())

library(tidyverse)
library(magrittr)
library(scales)
library(tidymodels)
library(corrplot)

theme_set(theme_minimal())

source("../src/kilnFunctions.R")
source("../src/userFunctions.R")

# import data -------------------------------------------------------------
df_merged    <- read_csv("../data/processed_data/df_merged.csv")
df_yields    <- read_csv("../data/processed_data/df_yields.csv")
df_defects   <- read_csv("../data/processed_data/df_defects.csv")

allAucValues <- read_csv("../data/processed_data/kilnsAucValues.csv")

# kilns_AB     <- read_csv("data/processed_data/kilns_AB.csv") %>% mutate_if(is.character,as.factor)
kilns_C      <- read_csv("../data/processed_data/kilns_C.csv")  %>% mutate_if(is.character,as.factor)
kilns_D      <- read_csv("../data/processed_data/kilns_D.csv")  %>% mutate_if(is.character,as.factor)
kilns_E      <- read_csv("../data/processed_data/kilns_E.csv")  %>% mutate_if(is.character,as.factor)
kilns_F      <- read_csv("../data/processed_data/kilns_F.csv")  %>% mutate(kiln = "F") %>% mutate_if(is.character,as.factor) 
kilns_G      <- read_csv("../data/processed_data/kilns_G.csv")  %>% mutate_if(is.character,as.factor)
kilns_H      <- read_csv("../data/processed_data/kilns_H.csv")  %>% mutate_if(is.character,as.factor)

kilns_All <- bind_rows(kilns_C[c(1:10,22,23)], 
                        kilns_D[c(1:10,22,23)], 
                        kilns_E[c(1:10,22,23)], 
                        kilns_F[c(1:10,22,23)], 
                        kilns_G[c(1:10,31,32)], 
                        kilns_H[c(1:10,40,41)])
```

# Feature generation

Using the kiln pressure data we can generate features to aid in concreteley determining whether certain patterns produce better yields. Some of the features discussed include:  

  * Area between **setpoint** and **average kiln temperature** (completed)
  * Time spent at positive **pressure** between 0 and 1000 minutes (replaced)
  * During the time when the **average kiln temperature** <= 1200°F:  
    + Duration at positive ***pressure** (pressure >= 0)
    + Duration at negative ***pressure** (pressure <  0)
    + Duration when **(0.01 <= pressure <= 0.03)**
    + Standard deviation of **pressure**
    + Mean of **pressure**
    + Also: what percentage of time is spent at each of these ranges?
    

Area under the curve was originally going to be calculated but after some thought, time spent within the pressure ranges seemed a more useful metric. Could potentially revisit an AUC calculation later on.  

```{r}
press_calcs <- kilns_All %>% 
  group_by(LOTNO) %>% 
  mutate(
    
    # adust pressure max and min 
    pressure = case_when(pressure > .07 ~ .07,
                         pressure < -.07 ~ -.07,
                         TRUE ~ pressure
                         ),
    
    # find time index where temp reaches 1200F
    close_1200  = if_else( (time < index_max_temp), (abs(1200 - avg_kiln_temp)), NULL ))

# join time index to original
press_calcs <- left_join(press_calcs, press_calcs %>% 
                           group_by(LOTNO) %>% 
                           dplyr::summarise(index_1200F = which.min(close_1200))
                         )

press_calcs <- press_calcs %>% 
  group_by(LOTNO) %>% 
  mutate(
    
    # segregate pressures into positive and negative columns
    press_pos = if_else((pressure >= 0) & (time <= index_1200F), pressure, NULL),
    press_neg = if_else((pressure <  0) & (time <= index_1200F), pressure, NULL),
    # get all pressures below 1200F point for easy mean, sd calcs
    press_1200F = if_else(time <= index_1200F, pressure, NULL),

    # segregate pressures into range columns
    press_greater_03 = if_else((pressure >  .03) &                     (time <= index_1200F), pressure, NULL),
    press_betw_01_03 = if_else((pressure >= .01) & (pressure <= .03) & (time <= index_1200F), pressure, NULL),
    press_betw_00_01 = if_else((pressure <  .01) & (pressure >=   0) & (time <= index_1200F), pressure, NULL),
    press_less_00    = if_else((pressure <    0) &                     (time <= index_1200F), pressure, NULL),
    
    # add counter columns for easy aggregation of total times spent in range
    press_pos_count = if_else(!is.na(press_pos),1,0),
    press_neg_count = if_else(!is.na(press_neg),1,0),
    
    press_greater_03_count = if_else(!is.na(press_greater_03),1,0),
    press_betw_01_03_count = if_else(!is.na(press_betw_01_03),1,0),
    press_betw_00_01_count = if_else(!is.na(press_betw_00_01),1,0),
    press_less_00_count    = if_else(!is.na(press_less_00),1,0)
    
  ) %>% 
  # remove helper columns
  dplyr::select(-c(close_1200)) %>% 
  dplyr::select(c(LOTNO,index_max_temp,index_1200F,everything()))

# summarise times at pressures
press_summ <- press_calcs %>% 
  group_by(LOTNO) %>% 
  dplyr::summarise(

    # sum times at negative and positive pressure
    time_at_pos = sum(press_pos_count, na.rm=TRUE),
    time_at_neg = sum(press_neg_count, na.rm=TRUE),
    
    # get means and sd of pressures
    mean_press  = mean(press_1200F, na.rm=TRUE),
    sd_press    = sd(press_1200F,   na.rm=TRUE),

    # sum times at pressure ranges
    time_greater_03 = sum(press_greater_03_count, na.rm=TRUE),
    time_betw_01_03 = sum(press_betw_01_03_count, na.rm=TRUE),
    time_betw_00_01 = sum(press_betw_00_01_count, na.rm=TRUE),
    time_less_00    = sum(press_less_00_count,    na.rm=TRUE)
  )

# join summarised features to original pressure data for easy plotting and verification
press_joined <- left_join(press_calcs, press_summ) %>% 
  mutate(
    pct_time_at_pos     = time_at_pos/index_1200F,
    pct_time_at_neg     = time_at_neg/index_1200F,
    pct_time_greater_03 = time_greater_03/index_1200F,
    pct_time_betw_01_03 = time_betw_01_03/index_1200F,
    pct_time_betw_00_01 = time_betw_00_01/index_1200F,
    pct_time_less_00    = time_less_00/index_1200F
  ) %>% 
  # remove helper columns
  dplyr::select(-c(press_pos_count,
                   press_neg_count,
                   press_greater_03_count,
                   press_betw_01_03_count,
                   press_betw_00_01_count,
                   press_less_00_count,
                   press_1200F
  ))

# attached aucDiff to each df
press_summ <- left_join(press_summ, allAucValues)
press_joined <- left_join(press_joined, allAucValues)
```

# Visualize features {.tabset .tabset-pills .tabset-fade}

Quick visualization of randomly selected lots to verify that metrics seem to be produced correctly.  

## 1

```{r}
# sample random lots
sample <- sample(levels(kilns_All$LOTNO),4)
# scale and shift values for second y-axis
sec_y_scale=20000
sec_y_shift=1500

# plot
press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>% 
  
  # KILN TEMP, SETPOINT, PRESSURE
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # PRESSURE POINTS
  geom_point(aes(y=press_betw_01_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  # HLINES
  geom_hline(aes(yintercept = .0 * sec_y_scale + sec_y_shift),color='red')+
  geom_hline(aes(yintercept = .01 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
  geom_hline(aes(yintercept = .03 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
    # mean/sd
  # geom_hline(aes(yintercept = mean_press * sec_y_scale + sec_y_shift),            color = 'blue',linetype='dotdash',size=1)+
  # geom_hline(aes(yintercept = (mean_press+sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  # geom_hline(aes(yintercept = (mean_press-sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  
  # PRESSURE RIBBONS
  # geom_ribbon(aes(ymin = press_less_00 * sec_y_scale + sec_y_shift, ymax = 0 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # geom_ribbon(aes(ymin = 0.00 * sec_y_scale + sec_y_shift, ymax = press_betw_00_01 * sec_y_scale +sec_y_shift),fill='yellow3',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_betw_01_03 * sec_y_scale + sec_y_shift),fill='green',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_greater_03 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # zoom on ribbons
  # scale_x_continuous(limits = c(0,18.4*60))+
  # scale_y_continuous(limits = c(1250,2350))
    # setpoint, temp AUC ribbon
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+
  
  scale_y_continuous(name = "Kiln temp (F)",
                   breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                   sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                       name = "Pressure",
                                       breaks = seq(-.1,.1,.01)
                                       )
                   )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
                     )+
  
  # labels
  # AUC
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(aucDiff),
             aes(x = 60 * 30, y = -0.065 * sec_y_scale + sec_y_shift,
                 label = paste0( "AUC: ", round(aucDiff,0) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='pink',label.size=.1
             ) +
  # MEAN
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(mean_press),
             aes(x = 60 * 30, y = -0.02 * sec_y_scale + sec_y_shift,
                 label = paste0( "mean: ", round(mean_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue',label.size=.1
             ) +
  # SD
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(sd_press),
             aes(x = 60 * 30, y = -0.03 * sec_y_scale + sec_y_shift,
                 label = paste0( "sd: ", round(sd_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue2',label.size=.1
             ) +
  # POS PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_pos, pct_time_at_pos, index_1200F),
             aes(x = 60 * 72, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_pos, "m, ",
                                 mypercent(pct_time_at_pos))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey80',label.size=.1
  ) +
  # NEG PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_neg, pct_time_at_neg, index_1200F),
             aes(x = 60 * 72, y = -0.06 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_neg, "m, ",
                                 mypercent(pct_time_at_neg))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey90'
             )+
  # LESS 00
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_less_00, pct_time_less_00, index_1200F),
             aes(x = 60 * 72, y = -.02 * sec_y_scale + sec_y_shift,
                 label = paste0( time_less_00, "m, ",
                                 mypercent(pct_time_less_00))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             )+
  # BETW 00 01
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_00_01, pct_time_betw_00_01, index_1200F),
             aes(x = 60 * 72, y = 0.0 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_00_01, "m, ",
                                 mypercent(pct_time_betw_00_01))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='yellow3'
             ) +
  # BETW 01 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_01_03, pct_time_betw_01_03, index_1200F),
             aes(x = 60 * 72, y = .02 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_01_03, "m, ",
                                 mypercent(pct_time_betw_01_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='green'
             ) +
  # GREATER 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_greater_03, pct_time_greater_03, index_1200F),
             aes(x = 60 * 72, y = 0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_greater_03, "m, ",
                                 mypercent(pct_time_greater_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             ) +
  facet_wrap(~LOTNO)
```

## 2

```{r}
# sample random lots
sample <- sample(levels(kilns_All$LOTNO),4)
# scale and shift values for second y-axis
sec_y_scale=20000
sec_y_shift=1500

# plot
press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>% 
  
  # KILN TEMP, SETPOINT, PRESSURE
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # PRESSURE POINTS
  geom_point(aes(y=press_betw_01_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  # HLINES
  geom_hline(aes(yintercept = .0 * sec_y_scale + sec_y_shift),color='red')+
  geom_hline(aes(yintercept = .01 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
  geom_hline(aes(yintercept = .03 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
    # mean/sd
  # geom_hline(aes(yintercept = mean_press * sec_y_scale + sec_y_shift),            color = 'blue',linetype='dotdash',size=1)+
  # geom_hline(aes(yintercept = (mean_press+sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  # geom_hline(aes(yintercept = (mean_press-sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  
  # PRESSURE RIBBONS
  # geom_ribbon(aes(ymin = press_less_00 * sec_y_scale + sec_y_shift, ymax = 0 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # geom_ribbon(aes(ymin = 0.00 * sec_y_scale + sec_y_shift, ymax = press_betw_00_01 * sec_y_scale +sec_y_shift),fill='yellow3',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_betw_01_03 * sec_y_scale + sec_y_shift),fill='green',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_greater_03 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # zoom on ribbons
  # scale_x_continuous(limits = c(0,18.4*60))+
  # scale_y_continuous(limits = c(1250,2350))
    # setpoint, temp AUC ribbon
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+
  
  scale_y_continuous(name = "Kiln temp (F)",
                   breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                   sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                       name = "Pressure",
                                       breaks = seq(-.1,.1,.01)
                                       )
                   )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
                     )+
  
  # labels
  # AUC
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(aucDiff),
             aes(x = 60 * 30, y = -0.065 * sec_y_scale + sec_y_shift,
                 label = paste0( "AUC: ", round(aucDiff,0) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='pink',label.size=.1
             ) +
  # MEAN
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(mean_press),
             aes(x = 60 * 30, y = -0.02 * sec_y_scale + sec_y_shift,
                 label = paste0( "mean: ", round(mean_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue',label.size=.1
             ) +
  # SD
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(sd_press),
             aes(x = 60 * 30, y = -0.03 * sec_y_scale + sec_y_shift,
                 label = paste0( "sd: ", round(sd_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue2',label.size=.1
             ) +
  # POS PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_pos, pct_time_at_pos, index_1200F),
             aes(x = 60 * 72, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_pos, "m, ",
                                 mypercent(pct_time_at_pos))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey80',label.size=.1
  ) +
  # NEG PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_neg, pct_time_at_neg, index_1200F),
             aes(x = 60 * 72, y = -0.06 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_neg, "m, ",
                                 mypercent(pct_time_at_neg))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey90'
             )+
  # LESS 00
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_less_00, pct_time_less_00, index_1200F),
             aes(x = 60 * 72, y = -.02 * sec_y_scale + sec_y_shift,
                 label = paste0( time_less_00, "m, ",
                                 mypercent(pct_time_less_00))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             )+
  # BETW 00 01
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_00_01, pct_time_betw_00_01, index_1200F),
             aes(x = 60 * 72, y = 0.0 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_00_01, "m, ",
                                 mypercent(pct_time_betw_00_01))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='yellow3'
             ) +
  # BETW 01 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_01_03, pct_time_betw_01_03, index_1200F),
             aes(x = 60 * 72, y = .02 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_01_03, "m, ",
                                 mypercent(pct_time_betw_01_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='green'
             ) +
  # GREATER 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_greater_03, pct_time_greater_03, index_1200F),
             aes(x = 60 * 72, y = 0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_greater_03, "m, ",
                                 mypercent(pct_time_greater_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             ) +
  facet_wrap(~LOTNO)
```

## 3

```{r}
# sample random lots
sample <- sample(levels(kilns_All$LOTNO),4)
# scale and shift values for second y-axis
sec_y_scale=20000
sec_y_shift=1500

# plot
press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>% 
  
  # KILN TEMP, SETPOINT, PRESSURE
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # PRESSURE POINTS
  geom_point(aes(y=press_betw_01_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  # HLINES
  geom_hline(aes(yintercept = .0 * sec_y_scale + sec_y_shift),color='red')+
  geom_hline(aes(yintercept = .01 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
  geom_hline(aes(yintercept = .03 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
    # mean/sd
  # geom_hline(aes(yintercept = mean_press * sec_y_scale + sec_y_shift),            color = 'blue',linetype='dotdash',size=1)+
  # geom_hline(aes(yintercept = (mean_press+sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  # geom_hline(aes(yintercept = (mean_press-sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  
  # PRESSURE RIBBONS
  # geom_ribbon(aes(ymin = press_less_00 * sec_y_scale + sec_y_shift, ymax = 0 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # geom_ribbon(aes(ymin = 0.00 * sec_y_scale + sec_y_shift, ymax = press_betw_00_01 * sec_y_scale +sec_y_shift),fill='yellow3',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_betw_01_03 * sec_y_scale + sec_y_shift),fill='green',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_greater_03 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # zoom on ribbons
  # scale_x_continuous(limits = c(0,18.4*60))+
  # scale_y_continuous(limits = c(1250,2350))
    # setpoint, temp AUC ribbon
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+
  
  scale_y_continuous(name = "Kiln temp (F)",
                   breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                   sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                       name = "Pressure",
                                       breaks = seq(-.1,.1,.01)
                                       )
                   )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
                     )+
  
  # labels
  # AUC
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(aucDiff),
             aes(x = 60 * 30, y = -0.065 * sec_y_scale + sec_y_shift,
                 label = paste0( "AUC: ", round(aucDiff,0) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='pink',label.size=.1
             ) +
  # MEAN
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(mean_press),
             aes(x = 60 * 30, y = -0.02 * sec_y_scale + sec_y_shift,
                 label = paste0( "mean: ", round(mean_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue',label.size=.1
             ) +
  # SD
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(sd_press),
             aes(x = 60 * 30, y = -0.03 * sec_y_scale + sec_y_shift,
                 label = paste0( "sd: ", round(sd_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue2',label.size=.1
             ) +
  # POS PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_pos, pct_time_at_pos, index_1200F),
             aes(x = 60 * 72, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_pos, "m, ",
                                 mypercent(pct_time_at_pos))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey80',label.size=.1
  ) +
  # NEG PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_neg, pct_time_at_neg, index_1200F),
             aes(x = 60 * 72, y = -0.06 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_neg, "m, ",
                                 mypercent(pct_time_at_neg))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey90'
             )+
  # LESS 00
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_less_00, pct_time_less_00, index_1200F),
             aes(x = 60 * 72, y = -.02 * sec_y_scale + sec_y_shift,
                 label = paste0( time_less_00, "m, ",
                                 mypercent(pct_time_less_00))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             )+
  # BETW 00 01
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_00_01, pct_time_betw_00_01, index_1200F),
             aes(x = 60 * 72, y = 0.0 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_00_01, "m, ",
                                 mypercent(pct_time_betw_00_01))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='yellow3'
             ) +
  # BETW 01 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_01_03, pct_time_betw_01_03, index_1200F),
             aes(x = 60 * 72, y = .02 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_01_03, "m, ",
                                 mypercent(pct_time_betw_01_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='green'
             ) +
  # GREATER 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_greater_03, pct_time_greater_03, index_1200F),
             aes(x = 60 * 72, y = 0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_greater_03, "m, ",
                                 mypercent(pct_time_greater_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             ) +
  facet_wrap(~LOTNO)
```

## 4

```{r}
# sample random lots
sample <- sample(levels(kilns_All$LOTNO),1)
# scale and shift values for second y-axis
sec_y_scale=20000
sec_y_shift=1500

# plot
press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>% 
  
  # KILN TEMP, SETPOINT, PRESSURE
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # PRESSURE POINTS
  geom_point(aes(y=press_betw_01_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  # HLINES
  geom_hline(aes(yintercept = .0 * sec_y_scale + sec_y_shift),color='red')+
  geom_hline(aes(yintercept = .01 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
  geom_hline(aes(yintercept = .03 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
    # mean/sd
  # geom_hline(aes(yintercept = mean_press * sec_y_scale + sec_y_shift),            color = 'blue',linetype='dotdash',size=1)+
  # geom_hline(aes(yintercept = (mean_press+sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  # geom_hline(aes(yintercept = (mean_press-sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  
  # PRESSURE RIBBONS
  # geom_ribbon(aes(ymin = press_less_00 * sec_y_scale + sec_y_shift, ymax = 0 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # geom_ribbon(aes(ymin = 0.00 * sec_y_scale + sec_y_shift, ymax = press_betw_00_01 * sec_y_scale +sec_y_shift),fill='yellow3',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_betw_01_03 * sec_y_scale + sec_y_shift),fill='green',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_greater_03 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # zoom on ribbons
  # scale_x_continuous(limits = c(0,18.4*60))+
  # scale_y_continuous(limits = c(1250,2350))
    # setpoint, temp AUC ribbon
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+
  
  scale_y_continuous(name = "Kiln temp (F)",
                   breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                   sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                       name = "Pressure",
                                       breaks = seq(-.1,.1,.01)
                                       )
                   )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
                     )+
  
  # labels
  # AUC
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(aucDiff),
             aes(x = 60 * 30, y = -0.065 * sec_y_scale + sec_y_shift,
                 label = paste0( "AUC: ", round(aucDiff,0) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='pink',label.size=.1
             ) +
  # MEAN
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(mean_press),
             aes(x = 60 * 30, y = -0.02 * sec_y_scale + sec_y_shift,
                 label = paste0( "mean: ", round(mean_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue',label.size=.1
             ) +
  # SD
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(sd_press),
             aes(x = 60 * 30, y = -0.03 * sec_y_scale + sec_y_shift,
                 label = paste0( "sd: ", round(sd_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue2',label.size=.1
             ) +
  # POS PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_pos, pct_time_at_pos, index_1200F),
             aes(x = 60 * 72, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_pos, "m, ",
                                 mypercent(pct_time_at_pos))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey80',label.size=.1
  ) +
  # NEG PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_neg, pct_time_at_neg, index_1200F),
             aes(x = 60 * 72, y = -0.06 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_neg, "m, ",
                                 mypercent(pct_time_at_neg))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey90'
             )+
  # LESS 00
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_less_00, pct_time_less_00, index_1200F),
             aes(x = 60 * 72, y = -.02 * sec_y_scale + sec_y_shift,
                 label = paste0( time_less_00, "m, ",
                                 mypercent(pct_time_less_00))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             )+
  # BETW 00 01
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_00_01, pct_time_betw_00_01, index_1200F),
             aes(x = 60 * 72, y = 0.0 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_00_01, "m, ",
                                 mypercent(pct_time_betw_00_01))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='yellow3'
             ) +
  # BETW 01 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_01_03, pct_time_betw_01_03, index_1200F),
             aes(x = 60 * 72, y = .02 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_01_03, "m, ",
                                 mypercent(pct_time_betw_01_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='green'
             ) +
  # GREATER 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_greater_03, pct_time_greater_03, index_1200F),
             aes(x = 60 * 72, y = 0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_greater_03, "m, ",
                                 mypercent(pct_time_greater_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             ) +
  facet_wrap(~LOTNO)
```

## Distribution

Quick distribution check of new features.  

```{r}
# pivot data and plot histograms
press_summ %>%
  dplyr::select(-LOTNO) %>% 
  pivot_longer(cols = is.numeric) %>% 
  mutate_if(is.character, factor) %>% 
  ggplot(aes(x=value))+
  geom_freqpoly()+
  facet_wrap(~name, scales='free')
```

# Lot yield vs features

Are lot yields impacted by these features, and if so, how much?.  

```{r}
# Join all data first

# get lot yields by summarising fired and rejects
lot_yields <- 
  df_yields %>% 
    group_by(LOTNO) %>% 
    dplyr::summarise(
      lot_items_fired = sum(TOTAL_ITEM_FIRED),
      lot_items_rejected = sum(TOTAL_ITEM_REJECTED),
      lot_yield = (lot_items_fired - lot_items_rejected) / lot_items_fired
    ) %>% 
    dplyr::select(LOTNO, lot_yield)

# join with all features, remove 20 missing lot yield values
press_summ <- left_join(press_summ, lot_yields) %>% 
  na.omit()

# since lot_yields are so skewed, bin into quantiles
library(binr)

cut_yields <- bins.quantiles(press_summ$lot_yield,6,10)
cut_yield_vals <- bins.getvals(cut_yields)

press_summ_binned <- press_summ %>% 
  mutate(lot_yield_binned = case_when(
     lot_yield <  cut_yield_vals[[2]] ~                                    "F",
    (lot_yield >= cut_yield_vals[[2]] & lot_yield < cut_yield_vals[[3]]) ~ "E",
    (lot_yield >= cut_yield_vals[[3]] & lot_yield < cut_yield_vals[[4]]) ~ "D",
    (lot_yield >= cut_yield_vals[[4]] & lot_yield < cut_yield_vals[[5]]) ~ "C",
    (lot_yield >= cut_yield_vals[[5]] & lot_yield < cut_yield_vals[[6]]) ~ "B",
     lot_yield >= cut_yield_vals[[6]] ~                                    "A",
    TRUE ~                                                                 "0"
  ))
```

## Corrplot

Quick check for any linear correlations between variables shows very weak correlations between `lot_yield` and all features (p-value > 0.05).

```{r}
# correlation matrix
M <- press_summ %>% 
  select(-LOTNO) %>% 
  cor()

cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}

# matrix of the p-value of the correlation
p.mat <- cor.mtest(M)

corrplot(M, order="hclust", type='upper',
         p.mat = p.mat, sig.level = 0.05)
```

## Linear model {.tabset .tabset-pills}

### 1

Non-binned response, non-scaled predictors.  

```{r}
lm1 <- lm(lot_yield ~ ., 
          data = press_summ %>%
            select(-LOTNO,-time_at_pos,-time_at_neg))

summary(lm1)
```

### 2

Binned response, scaled & centered predictors.  

```{r}
press_recipe <- recipe(lot_yield ~ ., data = press_summ) %>% 
  update_role(LOTNO, new_role = "ID") %>% 
  step_normalize(all_predictors())
  
press_prep <- prep(press_recipe)

lm2 <- lm(lot_yield ~ ., 
          data = juice(press_prep) %>% 
            select(-LOTNO,-time_at_pos,-time_at_neg))

summary(lm2)
```

## RF Model

Try random forest to predict binned levels `A` thru `F` of `lot_yields`.  

```{r}
# train and test sets
set.seed(123)
press_split <- initial_split(press_summ_binned)
press_train <- training(press_split)
press_test <- testing(press_split)

# recipe
press_recipe <- recipe(lot_yield_binned ~ ., 
                       data = press_train %>% select(-lot_yield)) %>% 
  update_role(LOTNO, new_role = "ID") %>% 
  step_normalize(all_predictors())
# prep
press_prep <- prep(press_recipe)

# model specs
tune_spec <- rand_forest(
  mtry = tune(),
  trees = 1000, 
  min_n = tune()
  ) %>% 
  set_mode("classification") %>% 
  set_engine("ranger")

# workflow
tune_wf <- workflow() %>% 
  add_recipe(press_recipe) %>% 

# train hyperparameters
set.seed(234)
press_folds <- vfold_cv(press_train)

# doParallel::registerDoParallel()

set.seed(344)
tune_res <- tune_grid(
  tune_wf,
  resamples = press_folds,
  grid = 20
)

# tune_res %>% collect_metrics()
# tune_res %>% select_best(metric='accuracy')

tune_res %>% 
  collect_metrics() %>% 
  filter(.metric == "roc_auc") %>% 
  select(mean, min_n, mtry) %>% 
  pivot_longer(min_n:mtry,
               values_to = "value",
               names_to = "parameter") %>% 
  ggplot(aes(value,mean,color=parameter))+
  geom_point(show.legend=FALSE)+
  geom_line(show.legend=FALSE)+
  facet_wrap(~parameter,scales='free')

# select value ranges to tune again
rf_grid <- grid_regular(
  mtry(range = c(3,8)),
  min_n(range = c(20, 40)),
  levels = 5
  )
# tune again
set.seed(341)
regular_res <- tune_grid(
  tune_wf,
  resamples = press_folds,
  grid = rf_grid
)
regular_res %>% 
  collect_metrics() %>% 
  filter(.metric == "roc_auc") %>% 
  mutate(min_n = factor(min_n)) %>% 
  ggplot(aes(mtry,mean,color=min_n))+
  geom_line()+
  geom_point()
kll
best_auc <- select_best(regular_res, "roc_auc")

final_rf <- finalize_model(
  tune_spec,
  best_auc
)

library(vip)
final_rf %>% 
  set_engine("ranger", importance = "permutation") %>% 
  fit(lot_yield_binned ~ ., 
      data = juice(press_prep) %>% select(-LOTNO)) %>% 
  vip(geom='point')

final_wf <- workflow() %>% 
  add_recipe(press_recipe) %>% 
  add_model(final_rf)

final_res <- final_wf %>% 
  last_fit(press_split)
    

final_res %>% 
  collect_metrics()

```


```{r}
library(tidymodels)
library(randomForest)

# press_boot <- bootstraps(press_summ)

press_recipe <- recipe(lot_yield ~ ., data = press_summ) %>% 
  update_role(LOTNO, new_role = "ID") %>% 
  step_normalize(all_predictors())
  
press_prep <- prep(press_recipe)

juice(press_prep) %>% 
  dplyr::select(-LOTNO) %>% 
  pivot_longer(cols = is.numeric) %>% 
  mutate_if(is.character, factor) %>% 
  ggplot(aes(x=value))+
  geom_freqpoly()+
  facet_wrap(~name, scales='free')

rf_spec <- rand_forest(trees = 1000) %>% 
  set_mode("regression") %>% 
  set_engine("randomForest")
  
press_wf <- workflow() %>% 
  add_recipe(press_recipe) %>% 
  add_model(rf_spec)

press_wf

press_res <- fit_resamples(
  press_wf,
  resamples = press_boot,
  control = control_resamples(save_pred=TRUE,
                              verbose=TRUE)
)

press_res %>% collect_metrics()

press_res %>% collect_predictions()

library(vip)

rf_spec %>% 
  set_engine('ranger', importance = 'permutation') %>% 
  fit(lot_yield ~ ., data = juice(press_prep) %>% select(-LOTNO)) %>% 
  vip(geom = "point")

```

```{r}


lm1 <- lm(lot_yield ~ ., data=juice(press_prep) %>% select(-LOTNO))
summary(lm1)
```

## Modeling

Since the response data is skewed heavily we can bin values by quantile distribution.  




```{r}
glimpse(press_summ)

# get lot yields by summarising fired and rejects
lot_yields <- 
  df_yields %>% 
    group_by(LOTNO) %>% 
    dplyr::summarise(
      lot_items_fired = sum(TOTAL_ITEM_FIRED),
      lot_items_rejected = sum(TOTAL_ITEM_REJECTED),
      lot_yield = (lot_items_fired - lot_items_rejected) / lot_items_fired
    ) %>% 
    dplyr::select(LOTNO, lot_yield)

# join with features, remove 20 missing lot yield values
press_summ <- left_join(press_summ, lot_yields) %>% 
  na.omit()



```


