---
title: "Kiln Pressure Data"
author: "Edward Yu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: paper
    highlight: textmate
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo    = TRUE,
                      error   = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      cache   = TRUE,
                      fig.width = 8, fig.height = 8,
                      dpi = 180)
rm(list = ls())

setwd("I:/Code-CAD/R/FD_dashboard")

library(tidyverse)
library(magrittr)
library(scales)
library(tidymodels)
library(corrplot)
library(binr)
library(kableExtra)
library(gridExtra)
library(ggpointdensity)
library(vip)
library(glmnet)

# set theme
theme_set(theme_minimal())

source("src/kilnFunctions.R")
source("src/userFunctions.R")

# import data -------------------------------------------------------------
df_merged    <- read_csv("data/processed_data/df_merged.csv")
df_yields    <- read_csv("data/processed_data/df_yields.csv")
df_defects   <- read_csv("data/processed_data/df_defects.csv")

allAucValues <- read_csv("data/processed_data/kilnsAucValues.csv")

# kilns_AB     <- read_csv("data/processed_data/kilns_AB.csv") %>% mutate_if(is.character,as.factor)
kilns_C      <- read_csv("data/processed_data/kilns_C.csv")  %>% mutate_if(is.character,as.factor)
kilns_D      <- read_csv("data/processed_data/kilns_D.csv")  %>% mutate_if(is.character,as.factor)
kilns_E      <- read_csv("data/processed_data/kilns_E.csv")  %>% mutate_if(is.character,as.factor)
kilns_F      <- read_csv("data/processed_data/kilns_F.csv")  %>% mutate(kiln = "F") %>% mutate_if(is.character,as.factor) 
kilns_G      <- read_csv("data/processed_data/kilns_G.csv")  %>% mutate_if(is.character,as.factor)
kilns_H      <- read_csv("data/processed_data/kilns_H.csv")  %>% mutate_if(is.character,as.factor)

kilns_All <- bind_rows(kilns_C[c(1:10,22,23)], 
                        kilns_D[c(1:10,22,23)], 
                        kilns_E[c(1:10,22,23)], 
                        kilns_F[c(1:10,22,23)], 
                        kilns_G[c(1:10,31,32)], 
                        kilns_H[c(1:10,40,41)])
```

# Summary

**Feature generation**  
Generated new features using primarily pressure data from the kiln logs. These new features, along with weather data, were then merged with both lot yields and item yields to determine if any of these factors influence yields in any way.  

**Lot yields**  
With lot yields, LASSO regression was used to eliminate the least important variables on a per kiln basis. When testing for variable importance on each kiln, none of the generated features were determined to be beneficial to the model. In other words, simply using the mean value of the lot yield produced better results than including any of the generated features.  

**Item yields**  
Some of the top occurring items were also tested. Unfortunately, similar results were observed where most features end up being eliminated. In some cases, the variables show very minor importance, which upon further investigation seems to be due to outliers in the dataset.  

**Next?**  
Its appears that none of the features, when singled out, play a significant linear role in determination of yields, whether it be yields of entire kilns, or of specific items within the kilns.  

When looking at the *Feature plots* below, we ideally want to see a horizontal separation of the colored *Yields* points which would indicate that a change in that feature is responsible for a change in the yield value. Unfortunately, most of the below models indicate that a horizontal line (the mean yield value) has more predictive power than using any of the currently generated features.  

We may need to look at additional features. It's also possible there are more complex interactions between the features not accounted for in these models.  

# Feature generation

Using the kiln pressure data we can generate features and determine if they have an effect on yields. Some of the features discussed include:  

  * Area between **setpoint** and **average kiln temperature** (completed)
  * Time spent at positive **pressure** between 0 and 1000 minutes (replaced)
  * During the time when the **average kiln temperature** <= 1200°F:  
    + Duration at positive ***pressure** (pressure >= 0)
    + Duration at negative ***pressure** (pressure <  0)
    + Duration when **(0.01 <= pressure <= 0.03)**
    + Standard deviation of **pressure**
    + Mean of **pressure**
    + Add weather data once again?

Durations between **(0.01 <= pressure <= 0.03)** were split into: **(0.01 <= pressure < 0.02)** and **(0.02 <= pressure < 0.03)**.  

```{r}
press_calcs <- kilns_All %>% 
  group_by(LOTNO) %>% 
  mutate(
    
    # adust pressure max and min 
    pressure = case_when(pressure > .07 ~ .07,
                         pressure < -.07 ~ -.07,
                         TRUE ~ pressure
                         ),
    
    # find time index where temp reaches 1200F
    close_1200  = if_else( (time < index_max_temp), (abs(1200 - avg_kiln_temp)), NULL ))

# join time index to original
press_calcs <- left_join(press_calcs, press_calcs %>% 
                           group_by(LOTNO) %>% 
                           dplyr::summarise(index_1200F = which.min(close_1200))
                         )

press_calcs <- press_calcs %>% 
  group_by(LOTNO) %>% 
  mutate(
    
    # segregate pressures into positive and negative columns
    press_pos = if_else((pressure >= 0) & (time <= index_1200F), pressure, NULL),
    press_neg = if_else((pressure <  0) & (time <= index_1200F), pressure, NULL),
    # get all pressures below 1200F point for easy mean, sd calcs
    press_1200F = if_else(time <= index_1200F, pressure, NULL),
    
    # segregate pressures into range columns
    press_greater_03 = if_else((pressure >= .03) &                    (time <= index_1200F), pressure, NULL),
    press_betw_02_03 = if_else((pressure >= .02) & (pressure < .03) & (time <= index_1200F), pressure, NULL),
    press_betw_01_02 = if_else((pressure >= .01) & (pressure < .02) & (time <= index_1200F), pressure, NULL),
    press_betw_00_01 = if_else((pressure >=  .0) & (pressure < .01) & (time <= index_1200F), pressure, NULL),
    press_less_00    = if_else((pressure <    0) &                    (time <= index_1200F), pressure, NULL),
    
    # add counter columns for easy aggregation of total times spent in range
    press_pos_count = if_else(!is.na(press_pos),1,0),
    press_neg_count = if_else(!is.na(press_neg),1,0),
    
    press_greater_03_count = if_else(!is.na(press_greater_03),1,0),
    press_betw_02_03_count = if_else(!is.na(press_betw_02_03),1,0),
    press_betw_01_02_count = if_else(!is.na(press_betw_01_02),1,0),
    press_betw_00_01_count = if_else(!is.na(press_betw_00_01),1,0),
    press_less_00_count    = if_else(!is.na(press_less_00),1,0)
    
  ) %>% 
  # remove helper columns
  dplyr::select(-c(close_1200)) %>% 
  dplyr::select(c(LOTNO,index_max_temp,index_1200F,everything()))

# summarise times at pressures
press_summ <- press_calcs %>% 
  group_by(LOTNO) %>% 
  dplyr::summarise(

    # sum times at negative and positive pressure
    time_at_pos = sum(press_pos_count, na.rm=TRUE),
    time_at_neg = sum(press_neg_count, na.rm=TRUE),
    
    # get means and sd of pressures
    mean_press  = mean(press_1200F, na.rm=TRUE),
    sd_press    = sd(press_1200F,   na.rm=TRUE),

    # sum times at pressure ranges
    time_greater_03 = sum(press_greater_03_count, na.rm=TRUE),
    time_betw_02_03 = sum(press_betw_02_03_count, na.rm=TRUE),
    time_betw_01_02 = sum(press_betw_01_02_count, na.rm=TRUE),
    time_betw_00_01 = sum(press_betw_00_01_count, na.rm=TRUE),
    time_less_00    = sum(press_less_00_count,    na.rm=TRUE),
    
    # pos and neg AUC pressures
    AUC_pos_press = sum(press_pos, na.rm=TRUE),
    AUC_neg_press = sum(abs(press_neg), na.rm=TRUE)
    
  )

# join summarised features to original pressure data for easy plotting and verification
press_joined <- left_join(press_calcs, press_summ) %>% 
  mutate(
    pct_time_at_pos     = time_at_pos/index_1200F,
    pct_time_at_neg     = time_at_neg/index_1200F,
    pct_time_greater_03 = time_greater_03/index_1200F,
    pct_time_betw_02_03 = time_betw_02_03/index_1200F,
    pct_time_betw_01_02 = time_betw_01_02/index_1200F,
    pct_time_betw_00_01 = time_betw_00_01/index_1200F,
    pct_time_less_00    = time_less_00/index_1200F
  ) %>% 
  # remove helper columns
  dplyr::select(-c(press_pos_count,
                   press_neg_count,
                   press_greater_03_count,
                   press_betw_02_03_count,
                   press_betw_01_02_count,
                   press_betw_00_01_count,
                   press_less_00_count,
                   press_1200F
  ))

# attached aucDiff to each df
press_summ   <- left_join(press_summ, allAucValues)
press_joined <- left_join(press_joined, allAucValues)

# add kiln column for quick filtering
press_summ <- press_summ %>%
  mutate(kiln = as.factor(str_extract(LOTNO, "[:alpha:]"))) 

# add weather data as well..
press_summ <- df_yields %>% 
  group_by(LOTNO) %>% slice(1) %>% ungroup() %>% 
  dplyr::select(LOTNO, precip:temp_avg) %>% 
  right_join(press_summ)

# prepare lot yield metric
# get lot yields by summarising fired and rejects
lot_yields <- 
  df_yields %>% 
    group_by(LOTNO) %>% 
    dplyr::summarise(
      lot_items_fired = sum(TOTAL_ITEM_FIRED),
      lot_items_rejected = sum(TOTAL_ITEM_REJECTED),
      lot_yield = (lot_items_fired - lot_items_rejected) / lot_items_fired
    ) %>% 
    dplyr::select(LOTNO, lot_yield)

# join yields with features, remove 20 missing lot yield values
press_summ <- left_join(press_summ, lot_yields) %>% 
  na.omit()

# remove zero value lot yields as outliers
press_summ <- press_summ %>% 
  mutate(lot_yield = ifelse( (lot_yield < .5), NA, lot_yield)) %>% 
  na.omit()
```

# Visualize features {.tabset .tabset-pills .tabset-fade}

Quick visualization of randomly selected lots to verify that metrics seem to be produced correctly.  

## 1

```{r}
# sample random lots
set.seed(123)
sampleC <- sample(levels(kilns_C$LOTNO),1)
sampleD <- sample(levels(kilns_D$LOTNO),1)
sampleE <- sample(levels(kilns_E$LOTNO),1)
sampleF <- sample(levels(kilns_F$LOTNO),1)
sampleG <- sample(levels(kilns_G$LOTNO),2)
sampleH <- sample(levels(kilns_H$LOTNO),2)
sample <- c(sampleC, sampleD, sampleE, sampleF)

# scale and shift values for second y-axis
sec_y_scale=20000
sec_y_shift=1500

# plot
press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>% 
  
  # KILN TEMP, SETPOINT, PRESSURE
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # PRESSURE POINTS
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  # HLINES
  geom_hline(aes(yintercept = .0 * sec_y_scale + sec_y_shift),color='red')+
  geom_hline(aes(yintercept = .01 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
  geom_hline(aes(yintercept = .02 * sec_y_scale + sec_y_shift),color='green',linetype='dashed')+
  geom_hline(aes(yintercept = .03 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
    # mean/sd
  # geom_hline(aes(yintercept = mean_press * sec_y_scale + sec_y_shift),            color = 'blue',linetype='dotdash',size=1)+
  # geom_hline(aes(yintercept = (mean_press+sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  # geom_hline(aes(yintercept = (mean_press-sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  
  # PRESSURE RIBBONS
  # geom_ribbon(aes(ymin = press_less_00 * sec_y_scale + sec_y_shift, ymax = 0 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # geom_ribbon(aes(ymin = 0.00 * sec_y_scale + sec_y_shift, ymax = press_betw_00_01 * sec_y_scale +sec_y_shift),fill='yellow3',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_betw_01_03 * sec_y_scale + sec_y_shift),fill='green',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_greater_03 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # zoom on ribbons
  # scale_x_continuous(limits = c(0,18.4*60))+
  # scale_y_continuous(limits = c(1250,2350))
    # setpoint, temp AUC ribbon
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+
  
  scale_y_continuous(name = "Kiln temp (F)",
                   breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                   sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                       name = "Pressure",
                                       breaks = seq(-.1,.1,.01)
                                       )
                   )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
                     )+
  
  # labels
  # AUC
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(aucDiff),
             aes(x = 60 * 30, y = -0.065 * sec_y_scale + sec_y_shift,
                 label = paste0( "AUC: ", round(aucDiff,0) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='pink',label.size=.1
             ) +
  # MEAN
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(mean_press),
             aes(x = 60 * 30, y = -0.02 * sec_y_scale + sec_y_shift,
                 label = paste0( "mean: ", round(mean_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue',label.size=.1
             ) +
  # SD
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(sd_press),
             aes(x = 60 * 30, y = -0.03 * sec_y_scale + sec_y_shift,
                 label = paste0( "sd: ", round(sd_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue2',label.size=.1
             ) +
  # POS PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_pos, pct_time_at_pos, index_1200F),
             aes(x = 60 * 72, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_pos, "m, ",
                                 mypercent(pct_time_at_pos))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey80',label.size=.1
  ) +
  # NEG PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_neg, pct_time_at_neg, index_1200F),
             aes(x = 60 * 72, y = -0.06 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_neg, "m, ",
                                 mypercent(pct_time_at_neg))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey90'
             )+
  # LESS 00
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_less_00, pct_time_less_00, index_1200F),
             aes(x = 60 * 72, y = -.02 * sec_y_scale + sec_y_shift,
                 label = paste0( time_less_00, "m, ",
                                 mypercent(pct_time_less_00))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             )+
  # BETW 00 01
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_00_01, pct_time_betw_00_01, index_1200F),
             aes(x = 60 * 72, y = 0.0 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_00_01, "m, ",
                                 mypercent(pct_time_betw_00_01))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='yellow3'
             ) +
  # BETW 01 02
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_01_02, pct_time_betw_01_02, index_1200F),
             aes(x = 60 * 72, y = .015 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_01_02, "m, ",
                                 mypercent(pct_time_betw_01_02))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='green'
             ) +
  # BETW 02 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_02_03, pct_time_betw_02_03, index_1200F),
             aes(x = 60 * 72, y = .025 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_02_03, "m, ",
                                 mypercent(pct_time_betw_02_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='green3'
             ) +
  # GREATER 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_greater_03, pct_time_greater_03, index_1200F),
             aes(x = 60 * 72, y = 0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_greater_03, "m, ",
                                 mypercent(pct_time_greater_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             ) +
  facet_wrap(~LOTNO)
```

## 2

```{r}
# sample random lots
set.seed(8634)
sample <- sample(levels(kilns_All$LOTNO),4)

# plot
press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>% 
  
  # KILN TEMP, SETPOINT, PRESSURE
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # PRESSURE POINTS
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  # HLINES
  geom_hline(aes(yintercept = .0 * sec_y_scale + sec_y_shift),color='red')+
  geom_hline(aes(yintercept = .01 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
  geom_hline(aes(yintercept = .02 * sec_y_scale + sec_y_shift),color='green',linetype='dashed')+
  geom_hline(aes(yintercept = .03 * sec_y_scale + sec_y_shift),color='red',linetype='dashed')+
    # mean/sd
  # geom_hline(aes(yintercept = mean_press * sec_y_scale + sec_y_shift),            color = 'blue',linetype='dotdash',size=1)+
  # geom_hline(aes(yintercept = (mean_press+sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  # geom_hline(aes(yintercept = (mean_press-sd_press) * sec_y_scale + sec_y_shift), color = 'blue2',linetype='dotted',size=1)+
  
  # PRESSURE RIBBONS
  # geom_ribbon(aes(ymin = press_less_00 * sec_y_scale + sec_y_shift, ymax = 0 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # geom_ribbon(aes(ymin = 0.00 * sec_y_scale + sec_y_shift, ymax = press_betw_00_01 * sec_y_scale +sec_y_shift),fill='yellow3',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_betw_01_03 * sec_y_scale + sec_y_shift),fill='green',alpha=1)+
  # geom_ribbon(aes(ymin = 0.0 * sec_y_scale + sec_y_shift, ymax = press_greater_03 * sec_y_scale + sec_y_shift),fill='red',alpha=1)+
  # zoom on ribbons
  # scale_x_continuous(limits = c(0,18.4*60))+
  # scale_y_continuous(limits = c(1250,2350))
    # setpoint, temp AUC ribbon
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+
  
  scale_y_continuous(name = "Kiln temp (F)",
                   breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                   sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                       name = "Pressure",
                                       breaks = seq(-.1,.1,.01)
                                       )
                   )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
                     )+
  
  # labels
  # AUC
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(aucDiff),
             aes(x = 60 * 30, y = -0.065 * sec_y_scale + sec_y_shift,
                 label = paste0( "AUC: ", round(aucDiff,0) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='pink',label.size=.1
             ) +
  # MEAN
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(mean_press),
             aes(x = 60 * 30, y = -0.02 * sec_y_scale + sec_y_shift,
                 label = paste0( "mean: ", round(mean_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue',label.size=.1
             ) +
  # SD
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(sd_press),
             aes(x = 60 * 30, y = -0.03 * sec_y_scale + sec_y_shift,
                 label = paste0( "sd: ", round(sd_press,3) )
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='lightskyblue2',label.size=.1
             ) +
  # POS PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_pos, pct_time_at_pos, index_1200F),
             aes(x = 60 * 72, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_pos, "m, ",
                                 mypercent(pct_time_at_pos))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey80',label.size=.1
  ) +
  # NEG PRESS
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_at_neg, pct_time_at_neg, index_1200F),
             aes(x = 60 * 72, y = -0.06 * sec_y_scale + sec_y_shift,
                 label = paste0( time_at_neg, "m, ",
                                 mypercent(pct_time_at_neg))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='grey90'
             )+
  # LESS 00
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_less_00, pct_time_less_00, index_1200F),
             aes(x = 60 * 72, y = -.02 * sec_y_scale + sec_y_shift,
                 label = paste0( time_less_00, "m, ",
                                 mypercent(pct_time_less_00))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             )+
  # BETW 00 01
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_00_01, pct_time_betw_00_01, index_1200F),
             aes(x = 60 * 72, y = 0.0 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_00_01, "m, ",
                                 mypercent(pct_time_betw_00_01))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='yellow3'
             ) +
  # BETW 01 02
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_01_02, pct_time_betw_01_02, index_1200F),
             aes(x = 60 * 72, y = .015 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_01_02, "m, ",
                                 mypercent(pct_time_betw_01_02))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='green'
             ) +
  # BETW 02 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_betw_02_03, pct_time_betw_02_03, index_1200F),
             aes(x = 60 * 72, y = .025 * sec_y_scale + sec_y_shift,
                 label = paste0( time_betw_02_03, "m, ",
                                 mypercent(pct_time_betw_02_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='green3'
             ) +
  # GREATER 03
  geom_label(data = press_joined %>% dplyr::filter(LOTNO %in% sample) %>% distinct(time_greater_03, pct_time_greater_03, index_1200F),
             aes(x = 60 * 72, y = 0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( time_greater_03, "m, ",
                                 mypercent(pct_time_greater_03))
             ),
             label.padding = unit(0.2, "lines"),hjust=1,vjust=.5,fill='red'
             ) +
  facet_wrap(~LOTNO)
```


# Variable importance

## by Lot yield

Do any of these features have an impact on overall lot yields for each kiln? In general it seems the answer is still "maybe?".  

When fitting standard linear models using all available predictors (see table below), $adjusted R^2$ values are either low or negative. Low values indicate high probability that the effect is random (regardless of significant $p.values$ in the model), while negative values indicate that the resulting linear model is worse fitting than a horizontal line.  

Although low $p.values$ are often used for variable selection or pruning, the practice is frowned upon. We use LASSO regression (a type of linear regression) in this case which works by shrinking the coefficients of less significant variables.  

**Standard linear models**   

```{r}
# linear model on each kiln
df <- press_summ %>% 
  dplyr::select(-LOTNO, -time_at_pos, -time_at_neg, -temp_avg)

set.seed(234)
df_split <- initial_split(df)
df_train <- training(df_split)
df_test  <- testing(df_split)

lms <- df  %>% 
  nest(data = c(-kiln)) %>% 
  mutate(fit =       map(data, ~lm(lot_yield ~ ., data = .x)),
         tidied =    map(fit, tidy),
         glanced =   map(fit, glance),
         augmented = map(fit, augment)
         ) 

# glanced
lm_glance <- lms %>% 
  unnest(glanced) %>% 
  select(-data,-fit,-tidied,-augmented) %>% 
  select(kiln, adj.r.squared,AIC,BIC) %>% 
  arrange(-adj.r.squared) %>% 
  mutate_if(is.numeric, round, 5)

kable(lm_glance %>% 
        left_join(count(press_summ$kiln) %>% 
                    mutate(kiln = factor(x)) %>% 
                    select(kiln, freq)) %>% 
        select(kiln, freq, everything()),
      format="html") %>% 
  kable_styling(full_width=T)

lm_tidy <- lms %>% 
  unnest(tidied) %>% 
  select(-data,-fit,-glanced,-augmented) %>%
  arrange(kiln, p.value) %>% 
  mutate_if(is.numeric, round, 5) %>% 
  mutate(
    p.value = ifelse(p.value < .05, 
                     cell_spec(p.value,"html",color="red"),
                     cell_spec(p.value,"html",color="black"))
  )
```

### C {.tabset}

#### LASSO

```{r}
# filter kiln
Kiln = "C"

df <- press_summ %>% 
  dplyr::filter(kiln == Kiln) %>% 
  dplyr::select(precip:aucDiff, lot_yield, -time_greater_03)

# normalize all predictors
df_norm <- recipe(lot_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$lot_yield)
x = as.matrix(df_norm[-18])

# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0("Kiln ", Kiln, ", Variable Importance by LASSO"))

```

#### Linear

```{r}
kable(lm_tidy %>% dplyr::filter(kiln == "C"), 
      format="html",
      caption = paste0("Significant variables by p-value, adj.R^2: ",
                       round(lm_glance$adj.r.squared[[2]], 3)),
      escape = F) %>%
  pack_rows( index=c("Kiln C" = 16)) %>%
  kable_styling("striped", full_width=T)
```

#### Feature plots

```{r}
df %>% 
  mutate(Yields = case_when( lot_yield >= 0.95 ~ "over95",
                               lot_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=lot_yield))+
  geom_point(aes(fill=Yields),alpha=.6,shape=21,size=2)+
  scale_y_continuous(labels = percent_format())+
  facet_wrap(~measures,scales='free_x',nrow=5)+
  geom_smooth(method=lm, se=FALSE)
```

### D {.tabset}

#### LASSO

```{r}
# filter kiln
Kiln = "D"

df <- press_summ %>% 
  dplyr::filter(kiln == Kiln) %>% 
  dplyr::select(precip:aucDiff, lot_yield)

# normalize all predictors
df_norm <- recipe(lot_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$lot_yield)
x = as.matrix(df_norm[-19])

# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0("Kiln ", Kiln, ", Variable Importance by LASSO"))

```

#### Linear

```{r}
kable(lm_tidy %>% dplyr::filter(kiln == "D"), 
      format="html",
      caption = paste0("Significant variables by p-value, adj.R^2: ",
                       round(lm_glance$adj.r.squared[[1]], 3)),
      escape = F) %>%
  pack_rows( index=c("Kiln D" = 16)) %>%
  kable_styling("striped", full_width=T)

# D_pruned <- press_summ %>% 
#   dplyr::filter(kiln == "D") %>% 
#   dplyr::select(mean_press:aucDiff,lot_yield)
# 
# lm(lot_yield ~ ., data = D_pruned) %>% summary()
```

#### Feature plots

```{r}
df %>% 
  mutate(Yields = case_when( lot_yield >= 0.95 ~ "over95",
                               lot_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=lot_yield))+
  geom_point(aes(fill=Yields),alpha=.5,shape=21,size=2)+
  scale_y_continuous(labels = percent_format())+
  facet_wrap(~measures,scales='free_x',nrow=5)+
  geom_smooth(method=lm, se=FALSE)
```

### E {.tabset}

#### LASSO

```{r}
# filter kiln
Kiln = "E"

df <- press_summ %>% 
  dplyr::filter(kiln == Kiln) %>% 
  dplyr::select(precip:aucDiff, lot_yield)

# normalize all predictors
df_norm <- recipe(lot_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$lot_yield)
x = as.matrix(df_norm[-19])

# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))
  ggtitle(paste0("Kiln ", Kiln, ", Variable Importance by LASSO"))
```

#### Linear

No p-values when using all predictors due to number of observations being so low (and number of predictors being so high). Below model produced omitting weather data.  

```{r}
E_data <- press_summ %>% 
  dplyr::filter(kiln == "E") %>% 
  dplyr::select(mean_press:aucDiff, lot_yield)

E_lm <- lm(lot_yield ~ ., data = E_data)
E_summ <- E_lm %>% summary()


kable(lm(lot_yield ~ ., data = E_data) %>% 
        tidy() %>% 
        arrange(p.value),
      format="html",
      caption = paste0("Significant variables by p-value, adj.R^2: ",
                       round(E_summ$adj.r.squared, 3)),
      escape = F) %>%
  pack_rows( index=c("Kiln E" = 11)) %>%
  kable_styling("striped", full_width=T)
```

#### Feature plots

```{r}
df %>% 
  mutate(Yields = case_when( lot_yield >= 0.95 ~ "over95",
                               lot_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=lot_yield))+
  geom_point(aes(fill=Yields),alpha=.8,shape=21,size=2)+
  scale_y_continuous(labels = percent_format())+
  facet_wrap(~measures,scales='free_x',nrow=5)+
  geom_smooth(method=lm, se=FALSE)
```


### F {.tabset}

No significant features when using p-value as a metric.  

#### LASSO

```{r}
# filter kiln
Kiln = "F"

df <- press_summ %>% 
  dplyr::filter(kiln == Kiln) %>% 
  dplyr::select(precip:aucDiff, lot_yield)

# normalize all predictors
df_norm <- recipe(lot_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$lot_yield)
x = as.matrix(df_norm[-19])

# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0("Kiln ", Kiln, ", Variable Importance by LASSO"))

```

#### Linear

```{r}
kable(lm_tidy %>% dplyr::filter(kiln == "F"), 
      format="html",
      caption = paste0("Significant variables by p-value, adj.R^2: ",
                       round(lm_glance$adj.r.squared[[5]], 3)),
      escape = F) %>%
  pack_rows( index=c("Kiln F" = 16)) %>%
  kable_styling("striped", full_width=T)
```

#### Feature plots

```{r}
df %>% 
  mutate(Yields = case_when( lot_yield >= 0.95 ~ "over95",
                               lot_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=lot_yield))+
  geom_point(aes(fill=Yields),alpha=.5,shape=21,size=2)+
  scale_y_continuous(labels = percent_format())+
  facet_wrap(~measures,scales='free_x',nrow=5)+
  geom_smooth(method=lm, se=FALSE)
```

### G {.tabset}

#### LASSO

```{r}
# filter kiln
Kiln = "G"

df <- press_summ %>% 
  dplyr::filter(kiln == Kiln) %>% 
  dplyr::select(precip:aucDiff, lot_yield)

# normalize all predictors
df_norm <- recipe(lot_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$lot_yield)
x = as.matrix(df_norm[-19])

# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0("Kiln ", Kiln, ", Variable Importance by LASSO"))
```

#### Linear

```{r}
kable(lm_tidy %>% dplyr::filter(kiln == "G"), 
      format="html",
      caption = paste0("Significant variables by p-value, adj.R^2: ",
                       round(lm_glance$adj.r.squared[[3]], 3)),
      escape = F) %>%
  pack_rows( index=c("Kiln G" = 16)) %>%
  kable_styling("striped", full_width=T)
```

#### Feature plots

```{r}
df %>% 
  mutate(Yields = case_when( lot_yield >= 0.95 ~ "over95",
                               lot_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")) %>% 
  dplyr::filter(lot_yield > .4) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=lot_yield))+
  geom_point(aes(fill=Yields),alpha=.4,shape=21,size=2)+
  scale_y_continuous(labels = percent_format())+
  facet_wrap(~measures,scales='free_x',nrow=5)+
  geom_smooth(method=lm, se=FALSE)
```

### H {.tabset}

No significant features when using p-value as a metric.  

#### LASSO

```{r}
# filter kiln
Kiln = "H"

df <- press_summ %>% 
  dplyr::filter(kiln == Kiln) %>% 
  dplyr::select(precip:aucDiff, lot_yield)

# normalize all predictors
df_norm <- recipe(lot_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$lot_yield)
x = as.matrix(df_norm[-19])

# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0("Kiln ", Kiln, ", Variable Importance by LASSO"))
```

#### Linear

```{r}
kable(lm_tidy %>% dplyr::filter(kiln == "H"), 
      format="html",
      caption = paste0("Significant variables by p-value, adj.R^2: ",
                       round(lm_glance$adj.r.squared[[4]], 3)),
      escape = F) %>%
  pack_rows( index=c("Kiln H" = 16)) %>%
  kable_styling("striped", full_width=T)
```

#### Feature plots

```{r}
df %>% 
  mutate(Yields = case_when( lot_yield >= 0.95 ~ "over95",
                               lot_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=lot_yield))+
  geom_point(aes(fill=Yields),alpha=.5,shape=21,size=2)+
  scale_y_continuous(labels = percent_format())+
  facet_wrap(~measures,scales='free_x',nrow=5)+
  geom_smooth(method=lm, se=FALSE)
```

## by Item yield

Perform analysis on items rather than kilns. This may shed light on whether certain items produce better yields under different circumstances than others.  

```{r}
# df yields join with press summ ... do pressures impact yields of items?

# get item yields, join with pressure stats
item_yields <- df_yields %>% 
  dplyr::select(LOTNO, ITEM, DESCRIPTION, FIRE_DATE, total_item_pct_yield) %>% 
  na.omit() %>% 
  right_join(press_summ)
```

### Carpenter Filter {.tabset}

#### Item yield over time 

```{r}
item = "215.5MMBODX38MM,45PPI,PSZM,FEC,1/8\"FG"

item_df <- item_yields %>% 
  dplyr::filter(DESCRIPTION == "215.5MMBODX38MM,45PPI,PSZM,FEC,1/8\"FG") %>% 
  mutate(Yields = case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50"))

item_df %>%    
  ggplot(aes(x=FIRE_DATE,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=3, shape=21, alpha=.8)+
  geom_smooth(method=lm, se=FALSE)+
  geom_line(alpha=.2)+
  # theme(legend.position = "none")+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  scale_fill_brewer(type="qual",palette=2)+
  ggtitle(paste0(item))+
  labs(x="Fire date", y="Item yield")
```

#### LASSO

```{r}
df <- item_df %>% 
  dplyr::select(total_item_pct_yield:aucDiff)

# normalize all predictors
df_norm <- recipe(total_item_pct_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$total_item_pct_yield)
x = as.matrix(df_norm[-19])

set.seed(234)
# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

set.seed(234)
# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0(item, ", VI by LASSO"))
```

#### Feature plots

```{r}
item_df %>%  
  dplyr::select(total_item_pct_yield:Yields) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=2,shape=21,alpha=.8)+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  facet_wrap(~measures,scales='free_x')+
  geom_smooth(method=lm, se=FALSE)
```

#### Visualize kiln plots {.tabset}

##### All

```{r}
sample <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::select(LOTNO) %>% unlist()

sec_y_scale=20000
sec_y_shift=1500

press_joined_item <- press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>%
  left_join(
    item_yields %>% 
      dplyr::filter(DESCRIPTION == item) %>% 
      dplyr::select(LOTNO,total_item_pct_yield)
    ) %>% 
    mutate(classify = factor(case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")))

press_joined_item %>% 

  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### Yields > 95%
```{r}

press_joined_item %>% 

  dplyr::filter(classify == "over95") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

##### > 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "over50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### < 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "below50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

### .75"ODX.5",30PPI,AL99,SEC {.tabset}

#### Item yield over time 

```{r}
item <- count(item_yields$DESCRIPTION) %>% 
  arrange(-freq) %>% 
  slice(1) %>% 
  dplyr::select(x) %>% 
  unlist()

item_df <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  mutate(Yields = case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50"))

item_df %>%    
  ggplot(aes(x=FIRE_DATE,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=3, shape=21, alpha=.8)+
  geom_smooth(method=lm, se=FALSE)+
  geom_line(alpha=.2)+
  # theme(legend.position = "none")+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  scale_fill_brewer(type="qual",palette=2)+
  ggtitle(paste0(item))+
  labs(x="Fire date", y="Item yield")
```

#### LASSO

```{r}
df <- item_df %>% 
  dplyr::select(total_item_pct_yield:aucDiff)

# normalize all predictors
df_norm <- recipe(total_item_pct_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$total_item_pct_yield)
x = as.matrix(df_norm[-19])

set.seed(344)
# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

set.seed(344)
# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0(item, ", VI by LASSO"))
```

#### Feature plots

```{r}
item_df %>%  
  dplyr::select(total_item_pct_yield:Yields) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=2,shape=21,alpha=.8)+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  facet_wrap(~measures,scales='free_x')+
  geom_smooth(method=lm, se=FALSE)
```

#### Visualize kiln plots {.tabset}

##### All

```{r}

set.seed(5532)
a <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield < .5) %>% 
  select(LOTNO) %>% unlist() %>% as.vector()
set.seed(5532)
b <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield >= .95) %>% 
  select(LOTNO) %>% unlist() %>% sample(8) %>% as.vector()
set.seed(5532)
c <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter((total_item_pct_yield >.7) & (total_item_pct_yield < .95)) %>% 
  select(LOTNO)  %>% unlist() %>% sample(7) %>% as.vector()

sample <- c(a,b,c)

# sample <- item_yields %>% 
#   dplyr::filter(DESCRIPTION == item) %>% 
#   dplyr::select(LOTNO) %>% unlist() %>% 
#   sample(16)

sec_y_scale=20000
sec_y_shift=1500

press_joined_item <- press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>%
  left_join(
    item_yields %>% 
      dplyr::filter(DESCRIPTION == item) %>% 
      dplyr::select(LOTNO,total_item_pct_yield)
    ) %>% 
    mutate(classify = factor(case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")))

press_joined_item %>% 

  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

##### Yields > 95%
```{r}

press_joined_item %>% 

  dplyr::filter(classify == "over95") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

##### > 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "over50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

##### < 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "below50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

### 2"ODX.5",30PPI,PSZM,SEC {.tabset}

#### Item yield over time 

```{r}
item <- count(item_yields$DESCRIPTION) %>% 
  arrange(-freq) %>% 
  slice(7) %>% 
  dplyr::select(x) %>% 
  unlist()

item_df <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  mutate(Yields = case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50"))

item_df %>%    
  ggplot(aes(x=FIRE_DATE,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=3, shape=21, alpha=.8)+
  geom_smooth(method=lm, se=FALSE)+
  geom_line(alpha=.2)+
  # theme(legend.position = "none")+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  scale_fill_brewer(type="qual",palette=2)+
  ggtitle(paste0(item))+
  labs(x="Fire date", y="Item yield")
```

#### LASSO

```{r}
df <- item_df %>% 
  dplyr::select(total_item_pct_yield:aucDiff)

# normalize all predictors
df_norm <- recipe(total_item_pct_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$total_item_pct_yield)
x = as.matrix(df_norm[-19])

set.seed(344)
# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

set.seed(344)
# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0(item, ", VI by LASSO"))
```

#### Feature plots

```{r}
item_df %>%  
  dplyr::select(total_item_pct_yield:Yields) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=2,shape=21,alpha=.8)+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  facet_wrap(~measures,scales='free_x')+
  geom_smooth(method=lm, se=FALSE)
```

#### Visualize kiln plots {.tabset}

##### All

```{r}

set.seed(5532)
a <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield <= .5) %>% 
  select(LOTNO) %>% unlist() %>% as.vector()
set.seed(5532)
b <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield >= .95) %>% 
  select(LOTNO) %>% unlist() %>% sample(8) %>% as.vector()
set.seed(5532)
c <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter((total_item_pct_yield >.5) & (total_item_pct_yield < .95)) %>% 
  select(LOTNO)  %>% unlist() %>% sample(7) %>% as.vector()

sample <- c(a,b,c)

# sample <- item_yields %>% 
#   dplyr::filter(DESCRIPTION == item) %>% 
#   dplyr::select(LOTNO) %>% unlist() %>% 
#   sample(16)

sec_y_scale=20000
sec_y_shift=1500

press_joined_item <- press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>%
  left_join(
    item_yields %>% 
      dplyr::filter(DESCRIPTION == item) %>% 
      dplyr::select(LOTNO,total_item_pct_yield)
    ) %>% 
    mutate(classify = factor(case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")))

press_joined_item %>% 

  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### Yields > 95%
```{r}

press_joined_item %>% 

  dplyr::filter(classify == "over95") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

##### > 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "over50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### < 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "below50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```






























### 44MMODX26MMIDX15MM,45PPI,AL99,FC {.tabset}

#### Item yield over time 

```{r}
item <- count(item_yields$DESCRIPTION) %>% 
  arrange(-freq) %>% 
  slice(9) %>% 
  dplyr::select(x) %>% 
  unlist()

item_df <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  mutate(Yields = case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50"))

item_df %>%    
  ggplot(aes(x=FIRE_DATE,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=3, shape=21, alpha=.8)+
  geom_smooth(method=lm, se=FALSE)+
  geom_line(alpha=.2)+
  # theme(legend.position = "none")+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  scale_fill_brewer(type="qual",palette=2)+
  ggtitle(paste0(item))+
  labs(x="Fire date", y="Item yield")
```

#### LASSO

```{r}
df <- item_df %>% 
  dplyr::select(total_item_pct_yield:aucDiff)

# normalize all predictors
df_norm <- recipe(total_item_pct_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$total_item_pct_yield)
x = as.matrix(df_norm[-19])

set.seed(344)
# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

set.seed(344)
# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0(item, ", VI by LASSO"))
```

#### Feature plots

```{r}
item_df %>%  
  dplyr::select(total_item_pct_yield:Yields) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=2,shape=21,alpha=.8)+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  facet_wrap(~measures,scales='free_x')+
  geom_smooth(method=lm, se=FALSE)
```

#### Visualize kiln plots {.tabset}

##### All

```{r}

set.seed(5532)
a <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield <= .5) %>% 
  select(LOTNO) %>% unlist() %>% sample(6) %>% as.vector()
set.seed(5532)
b <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield >= .95) %>% 
  select(LOTNO) %>% unlist() %>% sample(4) %>% as.vector()
set.seed(5532)
c <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter((total_item_pct_yield >.5) & (total_item_pct_yield < .95)) %>% 
  select(LOTNO)  %>% unlist() %>% sample(6) %>% as.vector()

sample <- c(a,b,c)

# sample <- item_yields %>% 
#   dplyr::filter(DESCRIPTION == item) %>% 
#   dplyr::select(LOTNO) %>% unlist() %>% 
#   sample(16)

sec_y_scale=20000
sec_y_shift=1500

press_joined_item <- press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>%
  left_join(
    item_yields %>% 
      dplyr::filter(DESCRIPTION == item) %>% 
      dplyr::select(LOTNO,total_item_pct_yield)
    ) %>% 
    mutate(classify = factor(case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")))

press_joined_item %>% 

  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### Yields > 95%
```{r}

press_joined_item %>% 

  dplyr::filter(classify == "over95") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

##### > 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "over50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### < 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "below50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```































### 10 TODX2.5 3 STRIP,10 20PPI,PSZM,FEC {.tabset}

#### Item yield over time 

```{r}
item <- count(item_yields$DESCRIPTION) %>% 
  arrange(-freq) %>% 
  slice(12) %>% 
  dplyr::select(x) %>% 
  unlist()

item_df <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  mutate(Yields = case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50"))

item_df %>%    
  ggplot(aes(x=FIRE_DATE,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=3, shape=21, alpha=.8)+
  geom_smooth(method=lm, se=FALSE)+
  geom_line(alpha=.2)+
  # theme(legend.position = "none")+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  scale_fill_brewer(type="qual",palette=2)+
  ggtitle(paste0(item))+
  labs(x="Fire date", y="Item yield")
```

#### LASSO

```{r}
df <- item_df %>% 
  dplyr::select(total_item_pct_yield:aucDiff)

# normalize all predictors
df_norm <- recipe(total_item_pct_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$total_item_pct_yield)
x = as.matrix(df_norm[-19])

set.seed(344)
# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

set.seed(344)
# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0(item, ", VI by LASSO"))
```

#### Feature plots

```{r}
item_df %>%  
  dplyr::select(total_item_pct_yield:Yields) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=2,shape=21,alpha=.8)+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  facet_wrap(~measures,scales='free_x')+
  geom_smooth(method=lm, se=FALSE)
```

#### Visualize kiln plots {.tabset}

##### All

```{r}

set.seed(5532)
a <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield <= .5) %>% 
  select(LOTNO) %>% unlist() %>% sample(5) %>% as.vector()
set.seed(5532)
b <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield >= .95) %>% 
  select(LOTNO) %>% unlist() %>% sample(6) %>% as.vector()
set.seed(5532)
c <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter((total_item_pct_yield >.5) & (total_item_pct_yield < .95)) %>% 
  select(LOTNO)  %>% unlist() %>% sample(5) %>% as.vector()

sample <- c(a,b,c)

# sample <- item_yields %>% 
#   dplyr::filter(DESCRIPTION == item) %>% 
#   dplyr::select(LOTNO) %>% unlist() %>% 
#   sample(16)

sec_y_scale=20000
sec_y_shift=1500

press_joined_item <- press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>%
  left_join(
    item_yields %>% 
      dplyr::filter(DESCRIPTION == item) %>% 
      dplyr::select(LOTNO,total_item_pct_yield)
    ) %>% 
    mutate(classify = factor(case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")))

press_joined_item %>% 

  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### Yields > 95%
```{r}

press_joined_item %>% 

  dplyr::filter(classify == "over95") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

##### > 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "over50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### < 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "below50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```































### 6X6X1.2 SP,12.5MMC,PSZM {.tabset}

#### Item yield over time 

```{r}
item <- count(item_yields$DESCRIPTION) %>% 
  arrange(-freq) %>% 
  slice(17) %>% 
  dplyr::select(x) %>% 
  unlist()

item_df <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  mutate(Yields = case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50"))

item_df %>%    
  ggplot(aes(x=FIRE_DATE,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=3, shape=21, alpha=.8)+
  geom_smooth(method=lm, se=FALSE)+
  geom_line(alpha=.2)+
  # theme(legend.position = "none")+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  scale_fill_brewer(type="qual",palette=2)+
  ggtitle(paste0(item))+
  labs(x="Fire date", y="Item yield")
```

#### LASSO

```{r}
df <- item_df %>% 
  dplyr::select(total_item_pct_yield:aucDiff)

# normalize all predictors
df_norm <- recipe(total_item_pct_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$total_item_pct_yield)
x = as.matrix(df_norm[-19])

set.seed(344)
# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

set.seed(344)
# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0(item, ", VI by LASSO"))
```

#### Feature plots

```{r}
item_df %>%  
  dplyr::select(total_item_pct_yield:Yields) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=2,shape=21,alpha=.8)+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  facet_wrap(~measures,scales='free_x')+
  geom_smooth(method=lm, se=FALSE)
```

#### Visualize kiln plots {.tabset}

##### All

```{r}

set.seed(5532)
a <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield <= .5) %>% 
  select(LOTNO) %>% unlist() %>% sample(5) %>% as.vector()
set.seed(5532)
b <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield >= .95) %>% 
  select(LOTNO) %>% unlist() %>% sample(6) %>% as.vector()
set.seed(5532)
c <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter((total_item_pct_yield >.5) & (total_item_pct_yield < .95)) %>% 
  select(LOTNO)  %>% unlist() %>% sample(5) %>% as.vector()

sample <- c(a,b,c)

# sample <- item_yields %>% 
#   dplyr::filter(DESCRIPTION == item) %>% 
#   dplyr::select(LOTNO) %>% unlist() %>% 
#   sample(16)

sec_y_scale=20000
sec_y_shift=1500

press_joined_item <- press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>%
  left_join(
    item_yields %>% 
      dplyr::filter(DESCRIPTION == item) %>% 
      dplyr::select(LOTNO,total_item_pct_yield)
    ) %>% 
    mutate(classify = factor(case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")))

press_joined_item %>% 

  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### Yields > 95%
```{r}

press_joined_item %>% 

  dplyr::filter(classify == "over95") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

##### > 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "over50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### < 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "below50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```































### 7X7X1.25,12.5MMC,PSZM {.tabset}

#### Item yield over time 

```{r}
item <- count(item_yields$DESCRIPTION) %>% 
  arrange(-freq) %>% 
  slice(26) %>% 
  dplyr::select(x) %>% 
  unlist()

item_df <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  mutate(Yields = case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50"))

item_df %>%    
  ggplot(aes(x=FIRE_DATE,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=3, shape=21, alpha=.8)+
  geom_smooth(method=lm, se=FALSE)+
  geom_line(alpha=.2)+
  # theme(legend.position = "none")+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  scale_fill_brewer(type="qual",palette=2)+
  ggtitle(paste0(item))+
  labs(x="Fire date", y="Item yield")
```

#### LASSO

```{r}
df <- item_df %>% 
  dplyr::select(total_item_pct_yield:aucDiff)

# normalize all predictors
df_norm <- recipe(total_item_pct_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$total_item_pct_yield)
x = as.matrix(df_norm[-19])

set.seed(344)
# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

set.seed(344)
# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0(item, ", VI by LASSO"))
```

#### Feature plots

```{r}
item_df %>%  
  dplyr::select(total_item_pct_yield:Yields) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=2,shape=21,alpha=.8)+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  facet_wrap(~measures,scales='free_x')+
  geom_smooth(method=lm, se=FALSE)
```

#### Visualize kiln plots {.tabset}

##### All

```{r}

set.seed(532)
a <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield <= .5) %>% 
  select(LOTNO) %>% unlist() %>% sample(5) %>% as.vector()
set.seed(532)
b <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield >= .95) %>% 
  select(LOTNO) %>% unlist() %>% sample(5) %>% as.vector()
set.seed(552)
c <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter((total_item_pct_yield >.5) & (total_item_pct_yield < .95)) %>% 
  select(LOTNO)  %>% unlist() %>% sample(6) %>% as.vector()

sample <- c(a,b,c)

# sample <- item_yields %>% 
#   dplyr::filter(DESCRIPTION == item) %>% 
#   dplyr::select(LOTNO) %>% unlist() %>% 
#   sample(16)

sec_y_scale=20000
sec_y_shift=1500

press_joined_item <- press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>%
  left_join(
    item_yields %>% 
      dplyr::filter(DESCRIPTION == item) %>% 
      dplyr::select(LOTNO,total_item_pct_yield)
    ) %>% 
    mutate(classify = factor(case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")))

press_joined_item %>% 

  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### Yields > 95%
```{r}

press_joined_item %>% 

  dplyr::filter(classify == "over95") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

##### > 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "over50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### < 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "below50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```































### 4X4X1,12.5MMC,PSZM {.tabset}

#### Item yield over time 

```{r}
item <- count(item_yields$DESCRIPTION) %>% 
  arrange(-freq) %>% 
  slice(27) %>% 
  dplyr::select(x) %>% 
  unlist()

item_df <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  mutate(Yields = case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50"))

item_df %>%    
  ggplot(aes(x=FIRE_DATE,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=3, shape=21, alpha=.8)+
  geom_smooth(method=lm, se=FALSE)+
  geom_line(alpha=.2)+
  # theme(legend.position = "none")+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  scale_fill_brewer(type="qual",palette=2)+
  ggtitle(paste0(item))+
  labs(x="Fire date", y="Item yield")
```

#### LASSO

```{r}
df <- item_df %>% 
  dplyr::select(total_item_pct_yield:aucDiff)

# normalize all predictors
df_norm <- recipe(total_item_pct_yield ~ ., data = df) %>% 
  step_normalize(all_predictors()) %>%
  prep() %>% 
  juice()

# split predictors and responses
y = as.vector(df_norm$total_item_pct_yield)
x = as.matrix(df_norm[-19])

set.seed(344)
# find best lambda value
cv.glmmod   <- cv.glmnet(x,y,alpha=1)
# plot(cv.glmmod)
best.lambda <- cv.glmmod$lambda.min

set.seed(344)
# produce model
glmmod <- glmnet(x, y, alpha=1, lambda = best.lambda)

# store coefficient values
coefs = data.frame(coef(glmmod)[,1])

# plot variable importance
tibble(data.frame(cbind(rownames(coefs), coefs))) %>% 
  set_colnames(c("Variable", "Importance")) %>% 
  mutate(Sign = if_else(Importance < 0, "Neg", "Pos"),
         Importance = abs(Importance),
         Variable = fct_reorder(Variable, Importance),
         HJ = if_else(Importance > .5, 1,0)) %>% 
  arrange(-Importance) %>% 
  ggplot(aes(x=Importance,y=Variable,fill=Sign))+
  geom_col()+
  geom_text(aes(label=round(Importance,5), hjust=HJ))+
  ggtitle(paste0(item, ", VI by LASSO"))
```

#### Feature plots

```{r}
item_df %>%  
  dplyr::select(total_item_pct_yield:Yields) %>% 
  pivot_longer(cols = precip:aucDiff, names_to = "measures", values_to="values") %>% 
  ggplot(aes(x=values,y=total_item_pct_yield))+
  geom_point(aes(fill=Yields),size=2,shape=21,alpha=.8)+
  scale_y_continuous(limits = c(0,1), labels = percent_format())+
  facet_wrap(~measures,scales='free_x')+
  geom_smooth(method=lm, se=FALSE)
```

#### Visualize kiln plots {.tabset}


##### All

```{r}

set.seed(532)
a <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield <= .5) %>% 
  select(LOTNO) %>% unlist() %>% sample(3) %>% as.vector()
set.seed(532)
b <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter(total_item_pct_yield >= .95) %>% 
  select(LOTNO) %>% unlist() %>% sample(6) %>% as.vector()
set.seed(552)
c <- item_yields %>% 
  dplyr::filter(DESCRIPTION == item) %>% 
  dplyr::filter((total_item_pct_yield >.5) & (total_item_pct_yield < .95)) %>% 
  select(LOTNO)  %>% unlist() %>% sample(7) %>% as.vector()

sample <- c(a,b,c)

# sample <- item_yields %>% 
#   dplyr::filter(DESCRIPTION == item) %>% 
#   dplyr::select(LOTNO) %>% unlist() %>% 
#   sample(16)

sec_y_scale=20000
sec_y_shift=1500

press_joined_item <- press_joined %>% 
  dplyr::filter(LOTNO %in% sample) %>%
  left_join(
    item_yields %>% 
      dplyr::filter(DESCRIPTION == item) %>% 
      dplyr::select(LOTNO,total_item_pct_yield)
    ) %>% 
    mutate(classify = factor(case_when( total_item_pct_yield >= 0.95 ~ "over95",
                               total_item_pct_yield >= 0.5 ~  "over50",
                               TRUE ~ "below50")))

press_joined_item %>% 

  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### Yields > 95%
```{r}

press_joined_item %>% 

  dplyr::filter(classify == "over95") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```

##### > 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "over50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```


##### < 50%

```{r}
press_joined_item %>% 

  dplyr::filter(classify == "below50") %>% 
  
  # kiln temp, setpoint, pressure
  ggplot(aes(x=time))+
  geom_line(aes(y=avg_kiln_temp))+
  geom_line(aes(y=setpoint),color='grey50',linetype='dashed')+
  geom_point(aes(y=pressure * sec_y_scale + sec_y_shift),alpha=.1,size=.1)+
  
  # color points
  geom_point(aes(y=press_greater_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  geom_point(aes(y=press_betw_02_03 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green3')+
  geom_point(aes(y=press_betw_01_02 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='green')+
  geom_point(aes(y=press_betw_00_01 * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='yellow2')+
  geom_point(aes(y=press_less_00    * sec_y_scale + sec_y_shift),alpha=1,size=.1,color='red')+
  
  geom_ribbon(aes(ymin = auc_min, ymax = auc_max),fill='pink',alpha=1)+

  scale_y_continuous(name = "Kiln temp (F)",
                     breaks = sort(c(seq(0,3000,1000),400,600,1200)),
                     sec.axis = sec_axis(~. / sec_y_scale - (sec_y_shift / sec_y_scale),
                                         name = "Pressure",
                                         breaks = seq(-.1,.1,.01)
                     )
  )+
  scale_x_continuous(name = "Hours", 
                     labels = number_format(scale=1/60),
                     breaks = sort(c(seq(0,100*60,12*60)))
  )+

  # yields
  geom_label(data = press_joined_item %>% dplyr::filter(LOTNO %in% sample) %>%
               distinct(total_item_pct_yield),
             aes(x = 60 * 65, y = -0.04 * sec_y_scale + sec_y_shift,
                 label = paste0( "Yield: ", mypercent(total_item_pct_yield) )
             ),
             label.padding = unit(0.2, "lines"),
             hjust=1,vjust=.5,
             fill='lightskyblue',
             label.size=.1
             ) +
  facet_wrap(~LOTNO)
```




























#